### 2023-07-25 Frictions Project/frictions_step1.tex
Idea phase

\documentclass[12pt]{article}
\usepackage[english]{babel}

% Set page size and margins
% Replace `letterpaper' with`a4paper' for UK/EU standard size
\usepackage[letterpaper,top=2cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}

% to typeset URLs, URIs, and DOIs
\usepackage[colorlinks=true, allcolors=blue]{hyperref}
\usepackage{url}
\usepackage{graphicx}
\usepackage[english]{babel}

% Bibliography
\usepackage[style=apa, backend=biber, natbib]{biblatex}
\addbibresource{../references.bib}
%\usepackage{natbib}

% useful packages
\usepackage{amsmath,amsfonts,amssymb,amsthm,mathtools,mathrsfs}
\usepackage{caption,subcaption}
\captionsetup{compatibility=false}
\usepackage{xcolor}
\usepackage{soul}
\usepackage{float}
\def\UrlFont{\rmfamily}

\renewcommand \thesection{\Roman{section}}
\renewcommand \thesubsection{\arabic{section}.\arabic{subsection}}

\begin{document}

\title{Research Project Step 1: Ideas}

\author{Mingxuan He\\
ECMA 33603\\
Prof. Andre Silva}
\date{\today}

\maketitle

%\tableofcontents

% For those that already have a thesis in progress:
% State the current title of your thesis and explain briefly, in one or two paragraphs, the objective of your thesis.
% List three ideas to add to your current MA project. Explain what you intend to do for each idea. The data that you will need or addition to the model that you will need to develop. Make clear how each idea will improve your current project.

\section*{Thesis topic description}
The title for my thesis is "Dynamic Modeling for Optimal Cryptoeconomic Policies". The objective is to construct a monetary model for cryptocurrency-based economies where the money supply can be adjusted in response to endogenous and exogenous shocks.\\
This research addresses the following gaps in the literature. Most current models feature a fixed or exogenous supply of tokens, which applies to the case for Bitcoin but not for most modern cryptocurrencies. On the other hand, traditional models for optimal fiscal policy (e.g. Ramsey) and monetary policy (e.g. New-Keynsian) are not directly transferrable to cryptoeconomies due to the additional frictions present in the latter. As of today, there has been no established literature on optimal economic policies for cryptocurrencies in general, despite some on CBDCs and stablecoins. \\
I will construct my model in extension to \citeauthor{biais2020equilibrium} (Journal of Finance 2020). They proposed a two-period general equilibrium asset pricing  model for Bitcoin with features including transaction fees as a friction, transactional benefits, and exogenous money supply. In the following sections, I present extensions and/or modifications to this model, most notably attempting to endogenize the money supply via the burning and staking mechanisms.

\section{Two-part transaction fee and burn mechanism}
In an attempt to prevent inflation, many protocols has adopted a burning mechanism by which some cryptocurrencies are permanently removed from supply (``burned"). One approach (e.g. Ethereum) is to have a two-part transaction fee system consisting of a base fee and a variable fee. Mathematically:
\[\varphi_t = \varphi^b_t + \varphi^v_t\]
where the base fee $\varphi^b_t$ is burned. $\varphi^v_t$ is often known as the ``tip" to block validators.\\
In \cite{biais2020equilibrium}, $\varphi_t$ is modeled as a single exogenous variable, and all fees are paid to the validators. Here in the two-part transaction fee system, $\varphi_t^v$ is exogeneously determined by the market for blockchain transactions, while $\varphi_t^b$ is endogenously controlled by the protocol. This allows the protocol to adjust the rate where money supply decreases. The fact that $\varphi^b_t$ also changes the transaction fee on cryptocurrencies is also similar to taxation.\\
The money supply equation with burning:
\begin{equation}
    M_{t+1} = M_t (1 - \varphi^b_t)
\end{equation}

\section{Interest-bearing staking}
Another key mechanism in modern (proof-of-stake) cryptoeconomies is staking rewards. When token holders stake their tokens in the protocol, the protocol rewards them with interest payments proportional to the amount staked. This interest is paid by minting new tokens, and the interest rate is controlled by the protocol. This mechanism serves as the main channel through which new tokens are injected into the economy (increasing money supply), as well as a relatively low-risk investment for token holders. The staked tokens presents a trade-off between liquidity and return to the token holders.\\
The money supply equation with staking:
\begin{equation}
    M_{t+1} = M_t + L_t r_t
\end{equation}
where $L_t$ is the amount of tokens staked in period $t$ and $r_t$ is the nominal interest rate controlled by the protocol.\\
Eqn.1 and 2 can be combined to have a money supply equation with both burning and staking:
\begin{equation}
    M_{t+1} = M_t (1 - \varphi^b_t) + L_t r_t
\end{equation}
The household's maximization problem will change to reflect a new decision between holding cryptocurrency as cash or staking them to earn interest (at the same time avoid being hacked). Note that they must give up transactional benefits (liquidity) in order to do so.

\section{A new method for estimating exogenous variables}
In \cite{biais2020equilibrium}, the amount of transactional benefits agents gain from holder cryptocurrencies is modeled as an exogenous process. In their calibration of the model, the data series on transactional benefits and fees are constructed by counting the events that likely affects the costs and benefits of using bitcoin, and summarize into two indices: \textit{MarketAccess} and \textit{Benefit}. Positive events have a +1 effect on the index, while negative events have a -1 effect.\\
I would like to find a more precise method for estimating these processes. Ideally, I'll be able to find data on the exact transaction fees on a cryptocurrency for a certain time period, to use as the exogenous fee variable. For transactional benefits, I can construct an index using a combination of market share, market capitalization, and number of active accounts (\cite{cong2021tokenomics, cong2022token}) to capture the network effect of the cryptocurrency platform on the transactional benefits and liquidity of the token.

\printbibliography

\end{document}

### 2023-07-25 Frictions Project/frictions_step2.tex
Idea phase

\documentclass[12pt]{article}
\usepackage[english]{babel}

% Set page size and margins
% Replace `letterpaper' with`a4paper' for UK/EU standard size
\usepackage[letterpaper,top=2cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}

% to typeset URLs, URIs, and DOIs
\usepackage[colorlinks=true, allcolors=blue]{hyperref}
\usepackage{url}
\usepackage{graphicx}
\usepackage[english]{babel}

% Bibliography
\usepackage[style=apa, backend=biber, natbib]{biblatex}
\addbibresource{../references.bib}
%\usepackage{natbib}

% useful packages
\usepackage{amsmath,amsfonts,amssymb,amsthm,mathtools,mathrsfs}
\usepackage{caption,subcaption}
\captionsetup{compatibility=false}
\usepackage{xcolor}
\usepackage{soul}
\usepackage{float}
\usepackage{tikz-cd}
\def\UrlFont{\rmfamily}

\renewcommand \thesection{\Roman{section}}
\renewcommand \thesubsection{\arabic{section}.\arabic{subsection}}

\begin{document}

\title{Dynamic Modeling for Optimal Cryptoeconomic Policies}

\author{Mingxuan He\\
ECMA 33603\\
Prof. Andre Silva
}

\maketitle

\begin{abstract}
    This paper introduces the idea of my thesis research project and documents my work so far. I provide a research topic description, discuss relevant literature including my replication for a baseline model, and report the current progress on my extended model, which combines two ideas from Stage 1 of the project.
\end{abstract}

%\tableofcontents

\section{Introduction}
In December 2018, the market capitalization of cryptocurrencies reached nearly 400 billion US Dollars, equivalent to 11\% of M1 in the USA \parencite{schilling2019some}. As the size of blockchain and cryptocurrency networks grew, there has been increasing discussion around volatility and welfare in cryptoeconomies, and ways for the issuer of the cryptocurrency protocol to implement policies to ensure there is sustainable benefits for the network of token holders. These policies are often referred to as the protocol's ``tokenomics".

As of today, most cryptoeconomic policies are static, which means the supply of tokens grows or shrinks according to a deterministic mechanism. For example, the supply of Bitcoin grows at a deterministic and decreasing rate. Many protocols cite these static policies act as an important aspect of decentralization: as the protocol pre-commits to a set of token issuance and burning policies, it reduces the requirement for trust from users in the procotol's governance. However, as demonstrated by both academic literature and recent events, the lack of response mechanisms can lead to devastating results when the cryptoeconomy faces exogenous shocks.

In many modern blockchain protocols, ``staking" and ``burning" are the primary coded policy rules in the underlying blockchain system. Staking is a mechanism where the user chooses to stake their token in the protocol for a period of time, after which the protocol rewards them with a staking yield that is paid out by newly minted tokens. In monetary economics terms, staking increases the total token supply by introducing new tokens into circulation, while reduces the amount of tokens in circulation due to illiquidity of the staked tokens. On the other hand, burning is a mechanism where the protocol burns (permanently destroys) some tokens from the supply, which usually comes from the transaction fees paid by users to conduct blockchain transactions.

Current staking and burning policy rules were primarily designed for the purpose of offering user incentives and/or preventing inflation from over-issuance. Most importantly, they do not respond to shock factors. My research aims to develop a model framework where staking and burning rules can be set dynamically to maximize the welfare of relevant actors in the cryptoeconomy.

This paper is organized as follows: Section \ref{sec:literature} provides an overview of the established literature. Section \ref{sec:model} outlines the baseline model by \citet{biais2020equilibrium} and replicates its solutions (\ref{sec:baseline}) and outlines the current progress of my extended model (\ref{sec:extensions}).

\section{Literature Review}
\label{sec:literature}
My research is related to the emerging literature on modeling cryptocurrencies and the blockchain economy. Following \citet{yermack2015bitcoin} that argued that Bitcoin is not a currency, there was an interest in studying Bitcoin as a financial asset. \citet{athey2016bitcoin, garratt2018bitcoin, biais2020equilibrium, pagnotta2022decentralizing} studied equilibria in asset pricing models for Bitcoin. \citet{schilling2019some, schilling2019currency} focused on the interactions between Bitcoin and the real economy, including dollar exchange rate and currency substitution. A broader set of models for Bitcoin include \citet{bolt2020value, catalini2020some, hinzen2022bitcoin, chiu2017economics, huberman2021monopoly}. For Proof-of-Stake protocols, \citet{saleh2019volatility, saleh2021blockchain} modeled their general volatility and welfare, while \citet{catalini2020markets} examined their tokenomics in the presence of an attack. A common result of the aforementioned asset pricing models is that static token supply causes all shocks are absorbed by the token price, which explains the high volatility of Bitcoin. This provides the motivation for an endogenous token supply in my model, which adds response mechanisms in terms of dynamic policy rules therefore can potentially mitigate the price effect of exogenous shocks.

Another set of literature has attempted to identify optimal policy rules for special types of tokens. \citet{cong2021tokenomics, cong2022token} built an asset pricing model featuring token issuance as means of platform financing and user growth leveraging network effects. \citet{sockin2023decentralization, sockin2023model} modeled cryptocurrencies as platform utility tokens and discussed elastic token issuance. \citet{d2022can} studied how stablecoin issuers can profit from seigniorage while maintaining the stablecoin's peg. \citet{fernandez2021central, zhu2019framework} are examples of papers proposing optimal monetary policies for CBDCs. While the policy goals of utility tokens are very specific (defending peg for stablecoins/CBDCs, making profit for stablecoins/platform tokens), I adopt the general policy goal of maximizing user welfare, measured by consumption and transactional benefits.

My research is also related to the large literature on cryptocurrencies. Notable empirical researches include \cite{liu2021risks} on the risk factors of cryptocurrencies, \cite{makarov2020trading} on the arbitrage spreads among different cryptocurrency markets. \cite{griffin2020bitcoin} studied the relationship between Tether purchases and cryptocurrency prices. Studies on the microeconomics of blockchain mechanisms include \citet{budish2018economic, biais2019blockchain, gans2019more, gans2022mechanism, huberman2021monopoly}.

\section{Model}
\label{sec:model}

\subsection{Baseline model}
\label{sec:baseline}
This model was proposed by \citeauthor*{biais2020equilibrium} in their 2020 paper in The Journal of Finance titled ``Equilibrium Bitcoin Pricing". Their main idea is that the fundamental value of cryptocurrencies comes from the stream of future transactional benefits (e.g. access to unique goods, not expropriated/taxed/constrained by government, direct internet access). The primary result is that Bitcoin price changes partly due to changes in fundamentals (net transactional benefits) but mostly due to extrinsic volatility.

The model is a two-period cryptoeconomy with overlapping generations of users. The cryptoeconomy includes three representative agents (user, validator, and hacker), three financial assets (risk-free asset, standard currency, and cryptocurrency). It features a fixed schedule money supply.

\subsubsection{Users}
In each period, young users receive some endowment in numeraire goods, which they spend on consumption goods and the three financial assets. They pay a fee on any cryptocurrency purchased. Old users consume all their savings from the previous period and receive transactional benefits on their cryptocurrencies. A portion of their crypto savings gets hacked. The users' budget constraints are:

\begin{align}
    c_t^y &= e_t- s_t - (1+\varphi_t) q_t p_t - \hat{q}_t \hat{p}_t\\
    c_{t+1}^o &= s_t (1+r_t) + (1-h_{t+1}) q_t p_{t+1} + \hat{q}_t \hat{p}_{t+1} \nonumber \\
    &+ \theta_{t+1} (1-h_{t+1}) q_t p_{t+1} 
\end{align}
\noindent
$e_t$: endowment\\
$s_t$: quantity of risk-free assets held\\
$q_t, \hat{q}_t$: quantities of crypto and dollars held\\
$p_t, \hat{p}_t$: prices (in units of consumption goods) of crypto and dollars\\
$h_{t+1}$: portion of crypto hacked by hackers\\
$\varphi_t$: transaction fees involved in using crypto (exog.)\footnote{The analysis remain largely unchanged if we include a transaction cost when selling crypto in period $t+1$ as well.}\\
$\theta_{t+1}$: transactional benefits from using crypto (exog.) (assume $\theta_{t+1}\geq-1$)

\subsubsection{Validators}
Validators receive newly minted tokens as block rewards, similar to a lump-sum transfer of money. The validators' budget constraint is:
\begin{align}
    c_{t+1}^v &= (X_{t+1} - X_t) p_{t+1} + \varphi_{t+1} q_{t+1} p_{t+1}
\end{align}
\noindent
$X_t$: stock token supply\\
$X_{t+1} - X_t$: increase in token supply (newly minted tokens)

\subsubsection{Hackers}
Hackers hack a portion of users' crypto. The hackers' budget constraint is:
\begin{align}
    c_{t+1}^h &= h_{t+1} q_t p_{t+1}
\end{align}

\noindent
I made a graph summarizing of the interaction of the agents in two periods: Figure \ref{fig:tikz-b}.

\begin{equation}
\label{fig:tikz-b}
\begin{tikzcd}[ampersand replacement=\&, column sep = 4.5em, row sep = 4.5em]
Protocol 
\ar[d, "\substack{\text{newly minted}\\\text{tokens}}" ']
\&
\ar[d, shift right, "\substack{\text{endow-}\\ \text{ment}}" 'near start]
\ar[d, shift left, "\substack{\text{purchase}\\ \text{assets}}" near start]
\&
\ar[d, "\substack{\text{transact.}\\ \text{benefits}}" ]
\&
\\
Validators
\& 
\substack{Young\\Users}
\ar[l,"\substack{\text{transact.}\\ \text{fees}}" ']
\ar[r, dashed, "t+1", 
"\substack{\text{hold}\\\text{assets}}" ']
\& 
\substack{Old\\Users}
\ar[r, "\substack{\text{hacked}\\ \text{tokens}}"]
\&
Hackers
\end{tikzcd}
\end{equation}

\subsubsection{Solution}
Here are my own steps for obtaining the pricing equations for cryptocurrency and standard currency.\\
The market clearing condition for the three financial assets are:
\begin{align}
    \text{crypto: } q_t &= X_t \\
    \text{dollars: } \hat{q}_t &= m \\
    \text{risk-free assets: } s_t &= 0 \\
\end{align}
Market for consumption goods also clears (by Walras's Law):
\begin{equation}
    c_t^y + c_t^o + c_t^v + c_t^h = e_t
\end{equation}
A young user in period $t$ solves:
\begin{align}
\max_{s_t, q_t, \hat{q}_t} &u(c_t^y) + \beta\mathbb{E}_t u(c_{t+1}^o)\\  
    \text{subject to  } & \text{user's budget constraints and } c_t^y \geq0 \nonumber
\end{align}
$^*$ Information set at period $t$ includes $ \{\theta_t, \varphi_t, \pi_t\}$ \\
The Lagrangian is
\begin{align}
    \mathcal{L} = &\ u(c_t^y) + \beta\mathbb{E}_t u(c_{t+1}^o) +\lambda c_t^y \nonumber \\ 
    = &\ u(e_t- s_t - (1+\varphi_t) q_t p_t - \hat{q}_t \hat{p}_t) \nonumber \\
    & + \beta \mathbb{E}_t\left[u(s_t (1+r_t) + (1-h_{t+1}) q_t p_{t+1} + \hat{q}_t \hat{p}_{t+1}
    + \theta_{t+1} (1-h_{t+1}) q_t p_{t+1}  ) \right] \nonumber \\
    & + \lambda (e_t- s_t - (1+\varphi_t) q_t p_t - \hat{q}_t \hat{p}_t)
\end{align}
First-order conditions:
\begin{align}
    s_t: & -u'(c_t^y) + \beta(1+r_t) \mathbb{E}_t[u'(c_{t+1}^o)] = \lambda\\
    q_t: & -(1+\varphi_t) p_t  u'(c_t^y) + \beta \mathbb{E}_t[u'(c_{t+1}^o)(1-h_{t+1})(1+\theta_{t+1})p_{t+1}] = \lambda (1+\varphi_t) p_t \\
    \hat{q}_t: & -\hat{p}_t u'(c_t^y) + \beta \mathbb{E}_t[u'(c_{t+1}^o) \hat{p}_{t+1}] = \lambda \hat{p}_t
\end{align}

\noindent
For Eqn. 14, substitute $\lambda$ with LHS of Eqn. 13:
\begin{align}
    &-(1+\varphi_t) p_t  u'(c_t^y) + \beta \mathbb{E}_t[u'(c_{t+1}^o)(1-h_{t+1})(1+\theta_{t+1})p_{t+1}] \nonumber \\
=&\ (1+\varphi_t)p_t
\{-u'(c_t^y) + \beta(1+r_t) \mathbb{E}_t[u'(c_{t+1}^o)]\} \\
\Rightarrow& \nonumber \\
&\beta \mathbb{E}_t[u'(c_{t+1}^o)(1-h_{t+1})(1+\theta_{t+1})p_{t+1}] \nonumber \\
=&\ (1+\varphi_t)p_t\beta(1+r_t) \mathbb{E}_t[u'(c_{t+1}^o)] \\
\Rightarrow & \nonumber \\
p_t=&\ \frac{1}{1+r_t} \frac{1}{1+\varphi_t}\mathbb{E}_t[u'(c_{t+1}^o)]^{-1} \mathbb{E}_t[u'(c_{t+1}^o)(1-h_{t+1})(1+\theta_{t+1})p_{t+1}]
\end{align}

Eqn. 18 is the pricing equation for cryptocurrency. Intuitively, $\frac{1}{1+r_t}$ is a discount by the interest rate, $1-h_{t+1}$ is the hack risk, $\frac{1+\theta_{t+1}}{1+\varphi_t}$ measures the net transactional benefits generating the currency's fundamental value, $\mathbb{E}_t[u'(c_{t+1}^o)]^{-1}u'(c_{t+1}^o)$ is the risk-neutral probability, and $p_{t+1}$ is the resale value. This pricing equation provides a viewpoint that Bitcoin prices reflect both fundamentals and extrinsic factors.

We can also consider Eqn. 15, and substitute $\lambda$ with LHS of Eqn. 13:
\begin{align}
&-\hat{p}_t u'(c_t^y) + \beta \mathbb{E}_t[u'(c_{t+1}^o) \hat{p}_{t+1}] \nonumber \\
=&\ \hat{p}_t \{-u'(c_t^y) + \beta(1+r_t) \mathbb{E}_t[u'(c_{t+1}^o)]\} \\
\Rightarrow& \nonumber \\
& \beta\mathbb{E}_t[u'(c_{t+1}^o) \hat{p}_{t+1}] \nonumber \\
=&\ \hat{p}_t \beta(1+r_t) \mathbb{E}_t[u'(c_{t+1}^o)] \\
\Rightarrow & \nonumber \\
\hat{p}_t =&\ \frac{1}{1+r_t} \mathbb{E}_t[u'(c_{t+1}^o)]^{-1} \mathbb{E}_t[u'(c_{t+1}^o) \hat{p}_{t+1}]
\end{align}

Eqn. 21 provides an expression for the return on dollars in the cryptoeconomy, in relation to the risk-neutral probability as well as the interest rate.

\subsection{Extended model}
\label{sec:extensions}
\subsubsection{Staking and burning}
In my extended model, I introduce two new mechanisms:
\begin{itemize}
    \item Two-part transaction fee with burning
    \item Interest-bearing staking
\end{itemize}
The protocol controls the staking yield (``interest rate") and the base transaction fee rate (burn rate). The figure below illustrates the new dynamics:
\begin{equation}
    \begin{tikzcd}[ampersand replacement=\&, column sep = 4.5em, row sep = 4.5em]
Protocol 
\ar[d, shift right, "\substack{\text{newly minted}\\\text{tokens}\\(t+1)}" ']
\&
\ar[d, shift right, "\substack{\text{endow-}\\\text{ment}}" 'near start]
\ar[d, shift left, "\substack{\text{purchase}\\ \text{assets}}" near start]
\&
\ar[d, "\substack{\text{transact.}\\ \text{benefits}}" ]
\&
\\
Validators
\ar[u, shift right, red, "\substack{\text{stake}\\\text{tokens}\\(t)}" ' red ]
\& 
\substack{Young\\Users}
\ar[l,"\substack{\text{variable}\\ \text{fees (``tip")}}" ']
\ar[lu, red, "\substack{\text{base fees}\\ \text{(burned)}}" {sloped,auto}' red]
\ar[r, dashed, "t+1", 
"\substack{\text{hold}\\\text{assets}}" ']
\& 
\substack{Old\\Users}
\ar[r, "\substack{\text{hacked}\\ \text{tokens}}"]
\&
Hackers
\end{tikzcd}
\end{equation}
Define new variables, following notation in the ideas step:\\
$L_t$: amount of staked tokens \\
$\delta_t$: staking yield (set by protocol)\\
$\varphi_t^b$: base fee (set by protocol)\\
$\varphi_t^v$: variable fee (competitively determined by validators and users)\\
The new budget constraints are:
\begin{align}
    \text{Young users: } c_t^y &= e_t - s_t - (1+{\color{red} \varphi_t^b+\varphi_t^v}) q_t p_t - \hat{q}_t \hat{p}_t\\
    \text{Old users: } c_{t+1}^o &=  s_t (1+r_t) + (1-h_{t+1}) q_t p_{t+1} + \hat{q}_t \hat{p}_{t+1} \nonumber \\
     &\hspace{2em} + \theta_{t+1} (1-h_{t+1}) q_t p_{t+1}\\ 
    \text{Validators: } c_{t+1}^v &= {\color{red} (1+\delta_t) L_t} p_{t+1} + {\color{red} \varphi_{t+1}^v} q_{t+1} p_{t+1} {\color{red} - L_{t+1} p_{t+1} }\\
    \text{Hackers: } c_{t+1}^h &= h_{t+1} q_t p_{t+1}
\end{align}

\subsubsection{Endogenous token supply}
Instead of a predetermined exogenous supply of tokens, now the supply is endogenous and dependent on the staking yield and base fee rate:
\begin{align}
    M_{t+1} &= (M_t - L_t) + L_t (1 + \delta_t) - \varphi_t^b X_t \nonumber \\
    &= M_t + \delta_t L_t - \varphi_t^b X_t
\end{align}
$M_t$: total token supply\\
$X_t \equiv M_t - L_t$: circulating supply (Now the market clearing condition is $X_t=q_t$)\\

\subsubsection{Validator's problem}
Since the amount staked is an active choice by the validators, we now have a new optimization problem by the validators:
\begin{align}
\max_{L_{t+1}}\ & u((1+\delta_t) L_t p_{t+1} + \varphi_{t+1}^v q_{t+1} p_{t+1} - L_{t+1}p_{t+1})\\
    \text{s.t. } & q_{t+1} \leq M_{t+1} - L_{t+1} \nonumber
\end{align}
This problem describes the following trade off by the validators:
\[
\text{more staking at } t \Rightarrow
\begin{cases}
    \text{more staking yield at } t+1\\
    \text{less circulating supply} \Rightarrow \text{less transact. fees at } t
\end{cases}
\]
Intuitively, the budget constraint should be binding since there should not be idle tokens in the economy: all tokens either enter the circulating supply or be staked to generate yields. Formally, we can apply Karush-Kuhn-Tucker to solve the optimization problem.

The solution to this problem, and a general equilibrium solution for the extended model, are currently work in progress.

\printbibliography

\end{document}

### 2023-07-25 Presentations/pitch_slides.tex
Idea phase

\documentclass{beamer}
\usepackage[utf8]{inputenc}

\usepackage{amsmath,amsfonts,amssymb,amsthm,
mathtools,mathrsfs}
\usepackage{physics}
\usepackage{xcolor}
\usepackage{hyperref}

\usepackage{tikz-cd} % arrow diagram

% Citation style
\usepackage[style=apa, backend=biber, natbib]{biblatex}
\addbibresource{../references.bib}

\usetheme{Madrid}
\usecolortheme{default}
\useoutertheme[subsection=false]{miniframes}
\setbeamertemplate{frametitle continuation}{}
\setbeamertemplate{bibliography item}[triangle]
\setbeamertemplate{sidebar right}{}
%\addtobeamertemplate{footnote}{}{\vspace{2ex}}

% Presenter notes
%\setbeameroption{show notes}

\title[Optimal Cryptoeconomic Policies]{Dynamic Modeling for Optimal Cryptoeconomic Policies}
\subtitle{Pitch Proposal 2}
\author{Mingxuan He}

\institute[UChicago]{
M.A. in Computational Social Science -- Economics\\
Department of Economics, University of Chicago\\
mingxuanh@uchicago.edu
}

\date{\today}

\begin{document}

% title page
\begin{frame}
\titlepage  
\end{frame}

% table of contents
% \begin{frame}
% \frametitle{Table of Contents}
% \tableofcontents
% \end{frame}

%----------------
\section{Introduction}

\begin{frame}{Research Question}

\textbf{How should we design dynamic staking and burning policies?}\newline
\begin{itemize}
\item Current protocol-coded policies are static even though crypto-economies face dynamic shocks. ``Staking" and ``burning" rates are the primary coded policy rules in the underlying blockchain system
\begin{itemize}
    \item \textbf{Staking (increases ``token supply", decreases ``tokens in circulation")}: mint new tokens and give to those who stake their existing tokens as interest. Similar to interest on reserves.
    \item \textbf{Burning (decreases ``token supply")}: burn (remove from circulation) a portion of the transaction fee paid by users during blockchain transactions
    \end{itemize} \textbf{}

    \item Policy goal: maximize welfare for \underline{good actors}: users (increase in token price) and validators (transaction fees)
\end{itemize}

\note{
shocks from the real economy: Banks failing, stock market, interest rates\\
shocks from other cryptoeconomies: Luna-Terra, FTX/Alameda
}

\end{frame}

%----------------
%\section{Literature Review}

\begin{frame}{Literature Review}
    \begin{itemize}
        \item Micro foundations:\\
        {\footnotesize \textit{\citet{nisan2007algorithmic, budish2018economic, biais2019blockchain, gans2019more, gans2022mechanism, huberman2021monopoly}, etc.}}\\
        $\rightarrow$ \textbf{Block reward and transaction fee as incentive mechanisms}

        \item Pricing models of cryptocurrencies:\\
        {\footnotesize Bitcoin: \textit{\citet{athey2016bitcoin, garratt2018bitcoin, schilling2019some, schilling2019currency, catalini2020some, biais2020equilibrium, bolt2020value, hinzen2022bitcoin, chiu2017economics}, etc.}}\\
        {\footnotesize Proof-of-stake: \textit{\citet{catalini2020markets, saleh2019volatility, saleh2021blockchain}}}\\
        $\rightarrow$ \textbf{Static token supply means all shocks are absorbed by price}
        \item Monetary policies for stablecoins, platform tokens, and CBDCs:\\
        {\footnotesize \textit{\citet{cong2021tokenomics, cong2022token, d2022can, fernandez2021central, zhu2019framework, sockin2023model, sockin2023decentralization}, etc.}}\\
        $\rightarrow$ \textbf{Optimizing policy for defending peg and/or making profit}
    \end{itemize}
\end{frame}

\begin{frame}{Contribution to the Literature}
\begin{itemize}
    \item Practical: Most cryptoeconomic systems feature fixed-schedule token supply
    \begin{itemize}
        \item deterministic token supply (Bitcoin\footnote{Satoshi Nakamoto (2008). Bitcoin: A peer-to-peer electronic cash system}), 
        fixed burn rate (Ethereum\footnote{Ethereum Documentation. ``Gas and Fees - Base fees"}), 
        naive dynamic burning (Binance Coin)
    \end{itemize}

    \item No published literature has been established on optimal staking and burning policies for proof-of-stake cryptocurrencies.
\end{itemize}
Novelty of this research:
\begin{itemize}
    \item Applies dynamic general equilibrium methods to model and optimize crypto policies for staking and burning            
      \item Traditional models for optimal fiscal policy (e.g. Ramsey) and monetary policy (e.g. NK) are not directly transferrable to cryptoeconomies due to transaction fee role in the cryptoeconomy

\end{itemize}
\end{frame}

%----------------
\section{Model (baseline)}
\begin{frame}{The baseline model (Biais et al. 2020, Journal of Finance)}
\textbf{Idea:} The fundamental value of crypto comes from the stream of future transactional benefits \parencite{tirole1985asset}\\
\begin{itemize}
    \item e.g. access to unique goods, not expropriated/taxed/constrained by government, direct internet access
\end{itemize}
\textbf{Setup:} Two-period model with overlapping generations
\begin{itemize}
    \item Three actors: users, validators (miners), hackers
    \item Three financial assets: a risk-free asset, a standard currency (dollar), a cryptocurrency (Bitcoin)
    \item Sources of shocks: endowment, transactional benefit, fees
\end{itemize}
\textbf{Result:} Bitcoin price changes partly due to changes in net transactional benefits, but mostly extrinsic volatility
\end{frame}

\begin{frame}{The baseline model (Biais et al. 2020, Journal of Finance)}
\[
\begin{tikzcd}[ampersand replacement=\&, column sep = 4.5em, row sep = 4.5em]
Protocol 
\ar[d, "\substack{\text{newly minted}\\\text{tokens}}" ']
\&
\ar[d, shift right, "\substack{\text{endow-}\\ \text{ment}}" 'near start]
\ar[d, shift left, "\substack{\text{purchase}\\ \text{assets}}" near start]
\&
\ar[d, "\substack{\text{transact.}\\ \text{benefits}}" ]
\&
\\
Validators
\& 
\substack{Young\\Users}
\ar[l,"\substack{\text{transact.}\\ \text{fees}}" ']
\ar[r, dashed, "t+1", 
"\substack{\text{hold}\\\text{assets}}" ']
\& 
\substack{Old\\Users}
\ar[r, "\substack{\text{hacked}\\ \text{tokens}}"]
\&
Hackers
\end{tikzcd}
\]
In each period: %\hyperlink{formal}{\beamerbutton{Formal Problem}}
\begin{itemize}
    \item \textbf{Young users} receive endowment, spend on consumption goods \& financial assets. Pay fees on crypto purchased
    \item \textbf{Old users} consume savings (some crypto savings get hacked), and receive transactional benefits
    \item \textbf{Validators} receive newly minted tokens as block rewards
    \item \textbf{Hackers} hack a portion of users' crypto
\end{itemize}
\end{frame}

\begin{frame}{The baseline model: Users}
\label{formal}
\begin{align}
    \text{Young users: } c_t^y &= e_t- s_t - (1+\varphi_t) q_t p_t - \hat{q}_t \hat{p}_t\\
    \text{Old users: } c_{t+1}^o &= s_t (1+r_t) + (1-h_{t+1}) q_t p_{t+1} + \hat{q}_t \hat{p}_{t+1} \nonumber \\
    &+ \theta_{t+1} (1-h_{t+1}) q_t p_{t+1} 
\end{align}

$e_t$: endowment\\
$s_t$: quantity of risk-free assets held\\
$q_t, \hat{q}_t$: quantities of crypto and dollars held\\
$p_t, \hat{p}_t$: prices (in units of consumption goods) of crypto and dollars\\
$h_{t+1}$: portion of crypto hacked by hackers\\
$\varphi_t$: transaction fees involved in using crypto (exog.)\footnote{The analysis remain largely unchanged if we include a transaction cost when selling crypto in period $t+1$ as well.}\\
$\theta_{t+1}$: transactional benefits from using crypto (exog.) (assume $\theta_{t+1}\geq-1$) \\

\end{frame}

\begin{frame}{The baseline model: Validators and hackers}
\begin{align}
    \text{Validators: } c_{t+1}^v &= (X_{t+1} - X_t) p_{t+1} + \varphi_{t+1} q_{t+1} p_{t+1}\\
    \text{Hackers: } c_{t+1}^h &= h_{t+1} q_t p_{t+1}
\end{align}
$X_t$: stock token supply\\
$X_{t+1} - X_t$: increase in token supply (newly minted tokens)
\end{frame}

\begin{frame}{The baseline model: Market clearing}
Markets for financial assets:
\begin{align}
    \text{crypto: } q_t &= X_t \\
    \text{dollars: } \hat{q}_t &= m \\
    \text{risk-free assets: } s_t &= 0 \\
\end{align}
Market for consumption goods (by Walras's Law):
\begin{equation}
    c_t^y + c_t^o + c_t^v + c_t^h = e_t
\end{equation}

\end{frame}

\begin{frame}{The baseline model: Solution}
A young user in period $t$ solves:
\begin{align}
\max_{s_t, q_t, \hat{q}_t} &u(c_t^y) + \beta\mathbb{E}_t u(c_{t+1}^o)\\  
    \text{subject to  } & \text{user's budget constraint} \nonumber
\end{align}
$^*$ Information set at period $t$ includes $ \{\theta_t, \varphi_t, \pi_t\}$ \\
From FOCs obtain the equilibrium pricing equation for crypto:
\newcommand{\vp}{\vphantom{\frac{u'(c_{t+1}^o)}{\mathbb{E}_t[u'(c_{t+1}^o)]}}}
\begin{equation}
    p_t = 
    \underbrace{\vp
    \frac{1}{1+r_t}}_\text{discount}
    \mathbb{E}_t \Bigl[ 
    \underbrace{\frac{u'(c_{t+1}^o)}{\mathbb{E}_t[u'(c_{t+1}^o)]}} _\text{risk-neutral prob}
    \underbrace{\vp
    (1-h_{t+1})} _\text{hack risk}
    \underbrace{\vp
    \frac{1+\theta_{t+1}}{1+\varphi_t}} _{\substack{\text{net transact.}\\ \text{benefits}}}
     p_{t+1}
    \Bigr]
\end{equation}    
\end{frame}

%----------------------------------
\section{Model (extended)}
\begin{frame}{Extension 1: Endogenous token supply}
\[
\begin{tikzcd}[ampersand replacement=\&, column sep = 4.5em, row sep = 4.5em]
Protocol 
\ar[d, shift right, "\substack{\text{newly minted}\\\text{tokens}\\(t+1)}" ']
\&
\ar[d, shift right, "\substack{\text{endow-}\\\text{ment}}" 'near start]
\ar[d, shift left, "\substack{\text{purchase}\\ \text{assets}}" near start]
\&
\ar[d, "\substack{\text{transact.}\\ \text{benefits}}" ]
\&
\\
Validators
\ar[u, shift right, red, "\substack{\text{stake}\\\text{tokens}\\(t)}" ' red ]
\& 
\substack{Young\\Users}
\ar[l,"\substack{\text{variable}\\ \text{fees (``tip")}}" ']
\ar[lu, red, "\substack{\text{base fees}\\ \text{(burned)}}" {sloped,auto}' red]
\ar[r, dashed, "t+1", 
"\substack{\text{hold}\\\text{assets}}" ']
\& 
\substack{Old\\Users}
\ar[r, "\substack{\text{hacked}\\ \text{tokens}}"]
\&
Hackers
\end{tikzcd}
\]
I introduce:
\begin{itemize}
    \item Two-part transaction fee with burning
    \item Interest-bearing staking
    \item The protocol controls the staking yield (``interest rate") and the base transaction fee rate (burn rate)
\end{itemize}
\end{frame}

\begin{frame}{Introducing staking and burning}
$^*$ The following is work in progress\\

\textbf{Staking:}
$L_t$: amount of staked tokens; $\delta_t$: staking yield (set by protocol)\\
\textbf{Burning:}
$\varphi_t^b$: base fee (set by protocol); $\varphi_t^v$: variable fee (competitively determined by validators and users)\\
\ \\
\textbf{New budget constraints:}
\begin{align}
    \text{Young users: } c_t^y &= e_t - s_t - (1+{\color{red} \varphi_t^b+\varphi_t^v}) q_t p_t - \hat{q}_t \hat{p}_t\\
    \text{Old users: } c_{t+1}^o &=  s_t (1+r_t) + (1-h_{t+1}) q_t p_{t+1} + \hat{q}_t \hat{p}_{t+1} \nonumber \\
     &\hspace{2em} + \theta_{t+1} (1-h_{t+1}) q_t p_{t+1}\\ 
    \text{Validators: } c_{t+1}^v &= {\color{red} (1+\delta_t) L_t} p_{t+1} + {\color{red} \varphi_{t+1}^v} q_{t+1} p_{t+1} {\color{red} - L_{t+1} p_{t+1} }\\
    \text{Hackers: } c_{t+1}^h &= h_{t+1} q_t p_{t+1}
\end{align}
\end{frame}

\begin{frame}{Token supply with staking and burning}
\begin{align}
    M_{t+1} &= (M_t - L_t) + L_t (1 + \delta_t) - \varphi_t^b X_t \nonumber \\
    &= M_t + \delta_t L_t - \varphi_t^b X_t
\end{align}
$M_t$: total token supply\\
$X_t \equiv M_t - L_t$: circulating supply \\
\quad $\Rightarrow$ Now market clearing condition is $X_t=q_t$\\
\ \\
$^*$ In reality the total reward is $\delta_t L_t^\alpha$, with pre-set $\alpha\in [0,1]$\footnote{$\alpha=0.5$ for Ethereum. See Ethereum Documentation. ``Proof-of-Stake Rewards and Penalties"}. Here I set $\alpha=1$ WLOG since $\delta_t$ is dynamic.
% calculations: https://blog.bitmex.com/ethereums-proof-of-stake-system-calculating-penalties-rewards/
\end{frame}

\begin{frame}{Validator's problem}
% should validators pay transaction fees when they cash out?
\begin{align}
\max_{L_{t+1}}\ & u((1+\delta_t) L_t p_{t+1} + \varphi_{t+1}^v q_{t+1} p_{t+1} - L_{t+1}p_{t+1})\\
    \text{s.t. } & q_{t+1} \leq M_{t+1} - L_{t+1} \nonumber
\end{align}
\textbf{Trade-off:}
\[
\text{more staking at } t \Rightarrow
\begin{cases}
    \text{more staking yield at } t+1\\
    \text{less circulating supply} \Rightarrow \text{less transact. fees at } t
\end{cases}
\]
Apply Karush-Kuhn-Tucker to solve the optimization problem
\end{frame}

%----------------
\section{Next Steps}
\begin{frame}{Next Steps}
    \begin{itemize}
        \item \textbf{The model:} Finish extended model with staking and burning, obtain analytical solution for equilibrium pricing, run simulations using dynare / Python\\
        \item \textbf{Replicate calibration:} Replicate calibration for baseline model (authors provided full replication code in Python)
        \item \textbf{Get data on Ethereum:} 
        \begin{itemize}
            \item ETH price data: Messari API\footnote{https://messari.io/api} (REST) and Dune Analytics\footnote{https://dune.com/docs/api} (SQL database with execution API in Python)
            \item ETH staking and burning data: Beacon Chain\footnote{https://ethereum.github.io/beacon-APIs} (REST)
        \end{itemize}
        \item \textbf{Calibrate my model}: get ideas after replicating calibration
    \end{itemize}
\end{frame}

% \begin{frame}{More extensions to model \& estimation}

% \begin{enumerate}
%     \item Modify validators' budget constraint: incorporates costs of validation under PoS and PoW \parencite{biais2019blockchain, saleh2019volatility, saleh2021blockchain}
%     \item Improvement in model calibration 
%     \begin{itemize}
%         \item novel time series data on Ethereum price and transaction fees
%         \item estimate transactional benefits using the NVT (network value to transaction ratio) or RVT (realized value to transaction ratio) metric instead of event-based index
%     \end{itemize}
%     \item Use vector autoregression models for exogenous process in variable transaction fees and transaction benefit (e.g. sign restrictions)
% \end{enumerate}
% \end{frame}

% \begin{frame}{Proposed Project Timeline}
% \begin{itemize}
%     \item Spring '23: As final project for ECMA33603 (Macro \& Financial Frictions), replicate the baseline model and implement extensions part 1 (endogenous token supply)
%     \item Summer '23: Implement extensions part 2; gather ideas from industry internship in Ethereum research \& dev
%     \item Fall '23 - Winter '24: Extensions part 3: Data collection, model calibration (likely using Ethereum data)
%     \item Spring '24: Finish paper
% \end{itemize}
% \end{frame}

% -----------------
\section*{}
\begin{frame}[allowframebreaks]{References}
    \nocite{*}
    %\bibliographystyle{apalike}
    %\bibliography{references}
    \printbibliography
\end{frame}

\end{document}

### 2023-07-25 literature_review.tex
Idea phase

\documentclass[12pt, a4paper]{article}
\usepackage[utf8]{inputenc}

\usepackage{amsmath,amsfonts,amssymb,amsthm,
mathtools,mathrsfs}
\usepackage{physics}
\usepackage{xcolor}
\usepackage{hyperref}
% Citation style
\usepackage[style=apa, backend=biber, natbib]{biblatex}
\addbibresource{references.bib}

\title{Literature review}
\author{Mingxuan He}

\begin{document}

\maketitle

\section*{Micro foundations}

\begin{itemize}
    \item \cite{nisan2007algorithmic}, etc. Algorithmic game theory
    \item \cite{gans2022mechanism}, etc. Mechanism design
    \item \cite{budish2018economic, gans2019more} Costs of securing blockchain
\end{itemize}

\section*{Pricing models of cryptocurrencies}
\begin{itemize}
    \item \cite{yermack2015bitcoin} Bitcoin is not a currency
    \item \cite{cong2021tokenomics, cong2022token} Asset pricing model featuring token issuance as means of platform financing and user growth
    \item \cite{athey2016bitcoin, catalini2020some} Partial equilibrium
    \item \cite{schilling2019some, schilling2019currency} Crypto vs. Fiat as mediums of exchange with transaction fees
    \item \cite{catalini2020markets} Demand and supply of PoS tokens under attack
    \item \cite{biais2020equilibrium} An OLG model of prices and transactional benefits
    \item \cite{bolt2020value} Modeled crypto exchange rates with quantity theory of money
\end{itemize}

\section*{Monetary policies for stablecoins, platform tokens, and CBDCs}

\end{document}

### 2023-09-23 Paper/main.tex
restructure documents

--- 2023-07-25 Frictions Project/frictions_step2.tex
@@
 
-% Set page size and margins
-% Replace `letterpaper' with`a4paper' for UK/EU standard size
 \usepackage[letterpaper,top=2cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}
@@
 \addbibresource{../references.bib}
-%\usepackage{natbib}
 
@@
 \usepackage{xcolor}
+\usepackage{csquotes}
 \usepackage{soul}
@@
 \usepackage{tikz-cd}
+\usepackage{subfiles}
 \def\UrlFont{\rmfamily}
@@
 \author{Mingxuan He\\
-ECMA 33603\\
-Prof. Andre Silva
 }
@@
 
-\begin{abstract}
-    This paper introduces the idea of my thesis research project and documents my work so far.
+% \begin{abstract}
+%     This paper introduces the idea of my thesis research project and documents my work so far.
 I provide a research topic description, discuss relevant literature including my replication for a baseline model, and report the current progress on my extended model, which combines two ideas from Stage 1 of the project.
-\end{abstract}
+% \end{abstract}
 
@@
 \section{Introduction}
+\label{sec:intro}
 In December 2018, the market capitalization of cryptocurrencies reached nearly 400 billion US Dollars, equivalent to 11\% of M1 in the USA \parencite{schilling2019some}.
@@
 Section \ref{sec:model} outlines the baseline model by \citet{biais2020equilibrium} and replicates its solutions (\ref{sec:baseline}) and outlines the current progress of my extended model (\ref{sec:extensions}).
+Section \ref{sec:data} describes the data I plan to use for calibration.
 
@@
 \label{sec:literature}
+% TODO: add new William Cong paper
 My research is related to the emerging literature on modeling cryptocurrencies and the blockchain economy.
@@
 
-\begin{equation}
-\label{fig:tikz-b}
-\begin{tikzcd}[ampersand replacement=\&, column sep = 4.5em, row sep = 4.5em]
-Protocol 
-\ar[d, "\substack{\text{newly minted}\\\text{tokens}}" ']
-\&
-\ar[d, shift right, "\substack{\text{endow-}\\ \text{ment}}" 'near start]
-\ar[d, shift left, "\substack{\text{purchase}\\ \text{assets}}" near start]
-\&
-\ar[d, "\substack{\text{transact.}\\ \text{benefits}}" ]
-\&
-\\
-Validators
-\& 
-\substack{Young\\Users}
-\ar[l,"\substack{\text{transact.}\\ \text{fees}}" ']
-\ar[r, dashed, "t+1", 
-"\substack{\text{hold}\\\text{assets}}" ']
-\& 
-\substack{Old\\Users}
-\ar[r, "\substack{\text{hacked}\\ \text{tokens}}"]
-\&
-Hackers
-\end{tikzcd}
-\end{equation}
+\subfile{../Figures/flowchart_baseline.tex}
 
@@
 The protocol controls the staking yield (``interest rate") and the base transaction fee rate (burn rate). The figure below illustrates the new dynamics:
-\begin{equation}
-    \begin{tikzcd}[ampersand replacement=\&, column sep = 4.5em, row sep = 4.5em]
-Protocol 
-\ar[d, shift right, "\substack{\text{newly minted}\\\text{tokens}\\(t+1)}" ']
-\&
-\ar[d, shift right, "\substack{\text{endow-}\\\text{ment}}" 'near start]
-\ar[d, shift left, "\substack{\text{purchase}\\ \text{assets}}" near start]
-\&
-\ar[d, "\substack{\text{transact.}\\ \text{benefits}}" ]
-\&
-\\
-Validators
-\ar[u, shift right, red, "\substack{\text{stake}\\\text{tokens}\\(t)}" ' red ]
-\& 
-\substack{Young\\Users}
-\ar[l,"\substack{\text{variable}\\ \text{fees (``tip")}}" ']
-\ar[lu, red, "\substack{\text{base fees}\\ \text{(burned)}}" {sloped,auto}' red]
-\ar[r, dashed, "t+1", 
-"\substack{\text{hold}\\\text{assets}}" ']
-\& 
-\substack{Old\\Users}
-\ar[r, "\substack{\text{hacked}\\ \text{tokens}}"]
-\&
-Hackers
-\end{tikzcd}
-\end{equation}
-Define new variables, following notation in the ideas step:\\
+
+\subfile{../Figures/flowchart_extended.tex}
+
+\noindent Define new variables as follows:\\
 $L_t$: amount of staked tokens \\
@@
 $\varphi_t^v$: variable fee (competitively determined by validators and users)\\
-The new budget constraints are:
+
+\noindent The new budget constraints are:
 \begin{align}
@@
 \end{align}
+
 This problem describes the following trade off by the validators:
@@
 \]
+
 Intuitively, the budget constraint should be binding since there should not be idle tokens in the economy: all tokens either enter the circulating supply or be staked to generate yields.
@@
 
+\section{Data}
+\label{sec:data}
+% move intro to ETH to introduction section later?
+The model describes the relationship between a cryptocurrency's prices and its transactional benefits, transaction costs, and hacking risks.
+As such, I choose the Ethereum blockchain, the second largest blockchain by size today, as the main cryptoeconomy of interest.
+It native token Ether (ETH) is the largest utility token and second largest cryptocurrency by market capitalization.
+
+Ether is the native token of the Ethereum protocol, which was originally founded in 2014 by Vitalik Buterin as a Proof-of-Work blockchain.
+In August 2021, the Ethereum blockchain implemented an upgrade referred to as Ethereum Improvement Proposal \#1559 or EIP-1559.
+EIP-1559 introduced a two-part transaction fee mechanism with an instantly-burned ``base fee" for their transactions to be included in the next block, and a ``priority fee" to pay validators for faster inclusion.
+In September 2022, Ethereum migrated from a Proof-of-Work (PoW) to Proof-of-Stake (PoS) consensus model (commonly known as ``the Merge"), mandating validator staking as the only source of new ETH tokens.
+Staking and burning together controls the supply of ETH on the blockchain.
+
+\subsection{Prices}
+% Do we need price data from many exchanges/denominations?
+The data set starts on September 16th, 2022, with the implementation of the Merge, and ends on September 31, 2023.
+I used time series data of daily ETH-USD prices provided by Messari\footnote{\url{https://messari.io/}}.
+For robustness checks, I follow \cite{biais2020equilibrium} to construct time series based on ETH prices denominated in five different currencies from 20 major exchanges.
+For non-USD denominations, I converted the prices using daily USD exchange rates data from Federal Reserve Economic Data (FRED).
+
+\subsection{Transaction fees}
+By design of the Ethereum blockchain, information on all historical transactions are publicly visible onchain.
+For each transaction, I retrieved its value and the associated base fee and priority fee through onchain data provider Dune Analytics\footnote{\url{https://dune.com/}}.
+Daily transaction volumes are computed by summing the value of all transactions in that day.
+Daily base fees and priority fees are computed by summing $BaseFee_i=GasUsed_i*BaseFeePerGas_j$ and $PriorityFee_i=GasUsed_i*PriorityFeePerGas_i$, respectively over each transaction $i$ in block $j$ produced in the day.
+Daily fee rates are then converted into percentages of the daily transaction volume.
+
+Admittedly, this simplified approach does not take into account self-transactions i.e.
+transfer of funds between different wallet addresses that belong to the same entity.
+Unfortunately due to the anonymity of the Ethereum blockchain, it is difficult to identify such self-transactions.
+% I will explore ways to overcome that as a robustness check.
+
+\subsection{Transaction benefits}
+% is this too endogenous? marketcap=price*supply; if so would switching to RVT (realized cap/txn volume) solve the problem??
+To measure the benefits of using ETH as a medium of transaction, I use a popular metric called Network Value to Transactions (NVT) ratio.
+The NVT ratio was originally constructed as an indicator for over- or under-priced tokens, similar to the P/E ratio for traditional equities.
+Intuitively, the NVT ratio measures how much an average user is willing to pay for a utility token for each unit of transaction volume denominated in that token.
+
+\subsection{Staking}
+Similar to transactions data, staking data has also been published in real-time on the Ethereum blockchain.
+I retrieved daily data on total ETH staked and ETH minted as validator rewards from open source Ethereum explorer beaconcha.in\footnote{\url{https://beaconcha.in}}.
+I then subtract any ETH burned as a result of slashing or other types of validator penalties from ETH minted.
+
+\newpage
 \printbibliography

### 2023-09-23 Figures/flowchart_baseline.tex
move flowcharts

--- 2023-07-25 Frictions Project/frictions_step2.tex
@@
-\documentclass[12pt]{article}
-\usepackage[english]{babel}
-
-% Set page size and margins
-% Replace `letterpaper' with`a4paper' for UK/EU standard size
-\usepackage[letterpaper,top=2cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}
-
-% to typeset URLs, URIs, and DOIs
-\usepackage[colorlinks=true, allcolors=blue]{hyperref}
-\usepackage{url}
-\usepackage{graphicx}
-\usepackage[english]{babel}
-
-% Bibliography
-\usepackage[style=apa, backend=biber, natbib]{biblatex}
-\addbibresource{../references.bib}
-%\usepackage{natbib}
-
-% useful packages
-\usepackage{amsmath,amsfonts,amssymb,amsthm,mathtools,mathrsfs}
-\usepackage{caption,subcaption}
-\captionsetup{compatibility=false}
-\usepackage{xcolor}
-\usepackage{soul}
-\usepackage{float}
-\usepackage{tikz-cd}
-\def\UrlFont{\rmfamily}
-
-\renewcommand \thesection{\Roman{section}}
-\renewcommand \thesubsection{\arabic{section}.\arabic{subsection}}
+\documentclass[../Paper/main.tex]{subfiles}
 
 \begin{document}
-
-\title{Dynamic Modeling for Optimal Cryptoeconomic Policies}
-
-\author{Mingxuan He\\
-ECMA 33603\\
-Prof. Andre Silva
-}
-
-\maketitle
-
-\begin{abstract}
-    This paper introduces the idea of my thesis research project and documents my work so far.
-I provide a research topic description, discuss relevant literature including my replication for a baseline model, and report the current progress on my extended model, which combines two ideas from Stage 1 of the project.
-\end{abstract}
-
-%\tableofcontents
-
-\section{Introduction}
-In December 2018, the market capitalization of cryptocurrencies reached nearly 400 billion US Dollars, equivalent to 11\% of M1 in the USA \parencite{schilling2019some}.
-As the size of blockchain and cryptocurrency networks grew, there has been increasing discussion around volatility and welfare in cryptoeconomies, and ways for the issuer of the cryptocurrency protocol to implement policies to ensure there is sustainable benefits for the network of token holders.
-These policies are often referred to as the protocol's ``tokenomics".
-
-As of today, most cryptoeconomic policies are static, which means the supply of tokens grows or shrinks according to a deterministic mechanism.
-For example, the supply of Bitcoin grows at a deterministic and decreasing rate.
-Many protocols cite these static policies act as an important aspect of decentralization: as the protocol pre-commits to a set of token issuance and burning policies, it reduces the requirement for trust from users in the procotol's governance.
-However, as demonstrated by both academic literature and recent events, the lack of response mechanisms can lead to devastating results when the cryptoeconomy faces exogenous shocks.
-
-In many modern blockchain protocols, ``staking" and ``burning" are the primary coded policy rules in the underlying blockchain system.
-Staking is a mechanism where the user chooses to stake their token in the protocol for a period of time, after which the protocol rewards them with a staking yield that is paid out by newly minted tokens.
-In monetary economics terms, staking increases the total token supply by introducing new tokens into circulation, while reduces the amount of tokens in circulation due to illiquidity of the staked tokens.
-On the other hand, burning is a mechanism where the protocol burns (permanently destroys) some tokens from the supply, which usually comes from the transaction fees paid by users to conduct blockchain transactions.
-
-Current staking and burning policy rules were primarily designed for the purpose of offering user incentives and/or preventing inflation from over-issuance.
-Most importantly, they do not respond to shock factors.
-My research aims to develop a model framework where staking and burning rules can be set dynamically to maximize the welfare of relevant actors in the cryptoeconomy.
-
-This paper is organized as follows: Section \ref{sec:literature} provides an overview of the established literature.
-Section \ref{sec:model} outlines the baseline model by \citet{biais2020equilibrium} and replicates its solutions (\ref{sec:baseline}) and outlines the current progress of my extended model (\ref{sec:extensions}).
-
-\section{Literature Review}
-\label{sec:literature}
-My research is related to the emerging literature on modeling cryptocurrencies and the blockchain economy.
-Following \citet{yermack2015bitcoin} that argued that Bitcoin is not a currency, there was an interest in studying Bitcoin as a financial asset.
-\citet{athey2016bitcoin, garratt2018bitcoin, biais2020equilibrium, pagnotta2022decentralizing} studied equilibria in asset pricing models for Bitcoin.
-\citet{schilling2019some, schilling2019currency} focused on the interactions between Bitcoin and the real economy, including dollar exchange rate and currency substitution.
-A broader set of models for Bitcoin include \citet{bolt2020value, catalini2020some, hinzen2022bitcoin, chiu2017economics, huberman2021monopoly}.
-For Proof-of-Stake protocols, \citet{saleh2019volatility, saleh2021blockchain} modeled their general volatility and welfare, while \citet{catalini2020markets} examined their tokenomics in the presence of an attack.
-A common result of the aforementioned asset pricing models is that static token supply causes all shocks are absorbed by the token price, which explains the high volatility of Bitcoin.
-This provides the motivation for an endogenous token supply in my model, which adds response mechanisms in terms of dynamic policy rules therefore can potentially mitigate the price effect of exogenous shocks.
-
-Another set of literature has attempted to identify optimal policy rules for special types of tokens.
-\citet{cong2021tokenomics, cong2022token} built an asset pricing model featuring token issuance as means of platform financing and user growth leveraging network effects.
-\citet{sockin2023decentralization, sockin2023model} modeled cryptocurrencies as platform utility tokens and discussed elastic token issuance.
-\citet{d2022can} studied how stablecoin issuers can profit from seigniorage while maintaining the stablecoin's peg.
-\citet{fernandez2021central, zhu2019framework} are examples of papers proposing optimal monetary policies for CBDCs.
-While the policy goals of utility tokens are very specific (defending peg for stablecoins/CBDCs, making profit for stablecoins/platform tokens), I adopt the general policy goal of maximizing user welfare, measured by consumption and transactional benefits.
-
-My research is also related to the large literature on cryptocurrencies.
-Notable empirical researches include \cite{liu2021risks} on the risk factors of cryptocurrencies, \cite{makarov2020trading} on the arbitrage spreads among different cryptocurrency markets.
-\cite{griffin2020bitcoin} studied the relationship between Tether purchases and cryptocurrency prices.
-Studies on the microeconomics of blockchain mechanisms include \citet{budish2018economic, biais2019blockchain, gans2019more, gans2022mechanism, huberman2021monopoly}.
-
-\section{Model}
-\label{sec:model}
-
-\subsection{Baseline model}
-\label{sec:baseline}
-This model was proposed by \citeauthor*{biais2020equilibrium} in their 2020 paper in The Journal of Finance titled ``Equilibrium Bitcoin Pricing".
-Their main idea is that the fundamental value of cryptocurrencies comes from the stream of future transactional benefits (e.g.
-access to unique goods, not expropriated/taxed/constrained by government, direct internet access).
-The primary result is that Bitcoin price changes partly due to changes in fundamentals (net transactional benefits) but mostly due to extrinsic volatility.
-
-The model is a two-period cryptoeconomy with overlapping generations of users.
-The cryptoeconomy includes three representative agents (user, validator, and hacker), three financial assets (risk-free asset, standard currency, and cryptocurrency).
-It features a fixed schedule money supply.
-
-\subsubsection{Users}
-In each period, young users receive some endowment in numeraire goods, which they spend on consumption goods and the three financial assets.
-They pay a fee on any cryptocurrency purchased.
-Old users consume all their savings from the previous period and receive transactional benefits on their cryptocurrencies.
-A portion of their crypto savings gets hacked.
-The users' budget constraints are:
-
-\begin{align}
-    c_t^y &= e_t- s_t - (1+\varphi_t) q_t p_t - \hat{q}_t \hat{p}_t\\
-    c_{t+1}^o &= s_t (1+r_t) + (1-h_{t+1}) q_t p_{t+1} + \hat{q}_t \hat{p}_{t+1} \nonumber \\
-    &+ \theta_{t+1} (1-h_{t+1}) q_t p_{t+1} 
-\end{align}
-\noindent
-$e_t$: endowment\\
-$s_t$: quantity of risk-free assets held\\
-$q_t, \hat{q}_t$: quantities of crypto and dollars held\\
-$p_t, \hat{p}_t$: prices (in units of consumption goods) of crypto and dollars\\
-$h_{t+1}$: portion of crypto hacked by hackers\\
-$\varphi_t$: transaction fees involved in using crypto (exog.)\footnote{The analysis remain largely unchanged if we include a transaction cost when selling crypto in period $t+1$ as well.}\\
-$\theta_{t+1}$: transactional benefits from using crypto (exog.) (assume $\theta_{t+1}\geq-1$)
-
-\subsubsection{Validators}
-Validators receive newly minted tokens as block rewards, similar to a lump-sum transfer of money. The validators' budget constraint is:
-\begin{align}
-    c_{t+1}^v &= (X_{t+1} - X_t) p_{t+1} + \varphi_{t+1} q_{t+1} p_{t+1}
-\end{align}
-\noindent
-$X_t$: stock token supply\\
-$X_{t+1} - X_t$: increase in token supply (newly minted tokens)
-
-\subsubsection{Hackers}
-Hackers hack a portion of users' crypto. The hackers' budget constraint is:
-\begin{align}
-    c_{t+1}^h &= h_{t+1} q_t p_{t+1}
-\end{align}
-
-\noindent
-I made a graph summarizing of the interaction of the agents in two periods: Figure \ref{fig:tikz-b}.
 
@@
 
-\subsubsection{Solution}
-Here are my own steps for obtaining the pricing equations for cryptocurrency and standard currency.\\
-The market clearing condition for the three financial assets are:
-\begin{align}
-    \text{crypto: } q_t &= X_t \\
-    \text{dollars: } \hat{q}_t &= m \\
-    \text{risk-free assets: } s_t &= 0 \\
-\end{align}
-Market for consumption goods also clears (by Walras's Law):
-\begin{equation}
-    c_t^y + c_t^o + c_t^v + c_t^h = e_t
-\end{equation}
-A young user in period $t$ solves:
-\begin{align}
-\max_{s_t, q_t, \hat{q}_t} &u(c_t^y) + \beta\mathbb{E}_t u(c_{t+1}^o)\\  
-    \text{subject to  } & \text{user's budget constraints and } c_t^y \geq0 \nonumber
-\end{align}
-$^*$ Information set at period $t$ includes $ \{\theta_t, \varphi_t, \pi_t\}$ \\
-The Lagrangian is
-\begin{align}
-    \mathcal{L} = &\ u(c_t^y) + \beta\mathbb{E}_t u(c_{t+1}^o) +\lambda c_t^y \nonumber \\ 
-    = &\ u(e_t- s_t - (1+\varphi_t) q_t p_t - \hat{q}_t \hat{p}_t) \nonumber \\
-    & + \beta \mathbb{E}_t\left[u(s_t (1+r_t) + (1-h_{t+1}) q_t p_{t+1} + \hat{q}_t \hat{p}_{t+1}
-    + \theta_{t+1} (1-h_{t+1}) q_t p_{t+1}  ) \right] \nonumber \\
-    & + \lambda (e_t- s_t - (1+\varphi_t) q_t p_t - \hat{q}_t \hat{p}_t)
-\end{align}
-First-order conditions:
-\begin{align}
-    s_t: & -u'(c_t^y) + \beta(1+r_t) \mathbb{E}_t[u'(c_{t+1}^o)] = \lambda\\
-    q_t: & -(1+\varphi_t) p_t  u'(c_t^y) + \beta \mathbb{E}_t[u'(c_{t+1}^o)(1-h_{t+1})(1+\theta_{t+1})p_{t+1}] = \lambda (1+\varphi_t) p_t \\
-    \hat{q}_t: & -\hat{p}_t u'(c_t^y) + \beta \mathbb{E}_t[u'(c_{t+1}^o) \hat{p}_{t+1}] = \lambda \hat{p}_t
-\end{align}
-
-\noindent
-For Eqn. 14, substitute $\lambda$ with LHS of Eqn. 13:
-\begin{align}
-    &-(1+\varphi_t) p_t  u'(c_t^y) + \beta \mathbb{E}_t[u'(c_{t+1}^o)(1-h_{t+1})(1+\theta_{t+1})p_{t+1}] \nonumber \\
-=&\ (1+\varphi_t)p_t
-\{-u'(c_t^y) + \beta(1+r_t) \mathbb{E}_t[u'(c_{t+1}^o)]\} \\
-\Rightarrow& \nonumber \\
-&\beta \mathbb{E}_t[u'(c_{t+1}^o)(1-h_{t+1})(1+\theta_{t+1})p_{t+1}] \nonumber \\
-=&\ (1+\varphi_t)p_t\beta(1+r_t) \mathbb{E}_t[u'(c_{t+1}^o)] \\
-\Rightarrow & \nonumber \\
-p_t=&\ \frac{1}{1+r_t} \frac{1}{1+\varphi_t}\mathbb{E}_t[u'(c_{t+1}^o)]^{-1} \mathbb{E}_t[u'(c_{t+1}^o)(1-h_{t+1})(1+\theta_{t+1})p_{t+1}]
-\end{align}
-
-Eqn.
-18 is the pricing equation for cryptocurrency.
-Intuitively, $\frac{1}{1+r_t}$ is a discount by the interest rate, $1-h_{t+1}$ is the hack risk, $\frac{1+\theta_{t+1}}{1+\varphi_t}$ measures the net transactional benefits generating the currency's fundamental value, $\mathbb{E}_t[u'(c_{t+1}^o)]^{-1}u'(c_{t+1}^o)$ is the risk-neutral probability, and $p_{t+1}$ is the resale value.
-This pricing equation provides a viewpoint that Bitcoin prices reflect both fundamentals and extrinsic factors.
-
-We can also consider Eqn. 15, and substitute $\lambda$ with LHS of Eqn. 13:
-\begin{align}
-&-\hat{p}_t u'(c_t^y) + \beta \mathbb{E}_t[u'(c_{t+1}^o) \hat{p}_{t+1}] \nonumber \\
-=&\ \hat{p}_t \{-u'(c_t^y) + \beta(1+r_t) \mathbb{E}_t[u'(c_{t+1}^o)]\} \\
-\Rightarrow& \nonumber \\
-& \beta\mathbb{E}_t[u'(c_{t+1}^o) \hat{p}_{t+1}] \nonumber \\
-=&\ \hat{p}_t \beta(1+r_t) \mathbb{E}_t[u'(c_{t+1}^o)] \\
-\Rightarrow & \nonumber \\
-\hat{p}_t =&\ \frac{1}{1+r_t} \mathbb{E}_t[u'(c_{t+1}^o)]^{-1} \mathbb{E}_t[u'(c_{t+1}^o) \hat{p}_{t+1}]
-\end{align}
-
-Eqn. 21 provides an expression for the return on dollars in the cryptoeconomy, in relation to the risk-neutral probability as well as the interest rate.
-
-\subsection{Extended model}
-\label{sec:extensions}
-\subsubsection{Staking and burning}
-In my extended model, I introduce two new mechanisms:
-\begin{itemize}
-    \item Two-part transaction fee with burning
-    \item Interest-bearing staking
-\end{itemize}
-The protocol controls the staking yield (``interest rate") and the base transaction fee rate (burn rate). The figure below illustrates the new dynamics:
-\begin{equation}
-    \begin{tikzcd}[ampersand replacement=\&, column sep = 4.5em, row sep = 4.5em]
-Protocol 
-\ar[d, shift right, "\substack{\text{newly minted}\\\text{tokens}\\(t+1)}" ']
-\&
-\ar[d, shift right, "\substack{\text{endow-}\\\text{ment}}" 'near start]
-\ar[d, shift left, "\substack{\text{purchase}\\ \text{assets}}" near start]
-\&
-\ar[d, "\substack{\text{transact.}\\ \text{benefits}}" ]
-\&
-\\
-Validators
-\ar[u, shift right, red, "\substack{\text{stake}\\\text{tokens}\\(t)}" ' red ]
-\& 
-\substack{Young\\Users}
-\ar[l,"\substack{\text{variable}\\ \text{fees (``tip")}}" ']
-\ar[lu, red, "\substack{\text{base fees}\\ \text{(burned)}}" {sloped,auto}' red]
-\ar[r, dashed, "t+1", 
-"\substack{\text{hold}\\\text{assets}}" ']
-\& 
-\substack{Old\\Users}
-\ar[r, "\substack{\text{hacked}\\ \text{tokens}}"]
-\&
-Hackers
-\end{tikzcd}
-\end{equation}
-Define new variables, following notation in the ideas step:\\
-$L_t$: amount of staked tokens \\
-$\delta_t$: staking yield (set by protocol)\\
-$\varphi_t^b$: base fee (set by protocol)\\
-$\varphi_t^v$: variable fee (competitively determined by validators and users)\\
-The new budget constraints are:
-\begin{align}
-    \text{Young users: } c_t^y &= e_t - s_t - (1+{\color{red} \varphi_t^b+\varphi_t^v}) q_t p_t - \hat{q}_t \hat{p}_t\\
-    \text{Old users: } c_{t+1}^o &=  s_t (1+r_t) + (1-h_{t+1}) q_t p_{t+1} + \hat{q}_t \hat{p}_{t+1} \nonumber \\
-     &\hspace{2em} + \theta_{t+1} (1-h_{t+1}) q_t p_{t+1}\\ 
-    \text{Validators: } c_{t+1}^v &= {\color{red} (1+\delta_t) L_t} p_{t+1} + {\color{red} \varphi_{t+1}^v} q_{t+1} p_{t+1} {\color{red} - L_{t+1} p_{t+1} }\\
-    \text{Hackers: } c_{t+1}^h &= h_{t+1} q_t p_{t+1}
-\end{align}
-
-\subsubsection{Endogenous token supply}
-Instead of a predetermined exogenous supply of tokens, now the supply is endogenous and dependent on the staking yield and base fee rate:
-\begin{align}
-    M_{t+1} &= (M_t - L_t) + L_t (1 + \delta_t) - \varphi_t^b X_t \nonumber \\
-    &= M_t + \delta_t L_t - \varphi_t^b X_t
-\end{align}
-$M_t$: total token supply\\
-$X_t \equiv M_t - L_t$: circulating supply (Now the market clearing condition is $X_t=q_t$)\\
-
-\subsubsection{Validator's problem}
-Since the amount staked is an active choice by the validators, we now have a new optimization problem by the validators:
-\begin{align}
-\max_{L_{t+1}}\ & u((1+\delta_t) L_t p_{t+1} + \varphi_{t+1}^v q_{t+1} p_{t+1} - L_{t+1}p_{t+1})\\
-    \text{s.t. } & q_{t+1} \leq M_{t+1} - L_{t+1} \nonumber
-\end{align}
-This problem describes the following trade off by the validators:
-\[
-\text{more staking at } t \Rightarrow
-\begin{cases}
-    \text{more staking yield at } t+1\\
-    \text{less circulating supply} \Rightarrow \text{less transact. fees at } t
-\end{cases}
-\]
-Intuitively, the budget constraint should be binding since there should not be idle tokens in the economy: all tokens either enter the circulating supply or be staked to generate yields.
-Formally, we can apply Karush-Kuhn-Tucker to solve the optimization problem.
-
-The solution to this problem, and a general equilibrium solution for the extended model, are currently work in progress.
-
-\printbibliography
-
 \end{document}

### 2023-09-23 Figures/flowchart_extended.tex
move flowcharts

--- 2023-07-25 Frictions Project/frictions_step2.tex
@@
-\documentclass[12pt]{article}
-\usepackage[english]{babel}
-
-% Set page size and margins
-% Replace `letterpaper' with`a4paper' for UK/EU standard size
-\usepackage[letterpaper,top=2cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}
-
-% to typeset URLs, URIs, and DOIs
-\usepackage[colorlinks=true, allcolors=blue]{hyperref}
-\usepackage{url}
-\usepackage{graphicx}
-\usepackage[english]{babel}
-
-% Bibliography
-\usepackage[style=apa, backend=biber, natbib]{biblatex}
-\addbibresource{../references.bib}
-%\usepackage{natbib}
-
-% useful packages
-\usepackage{amsmath,amsfonts,amssymb,amsthm,mathtools,mathrsfs}
-\usepackage{caption,subcaption}
-\captionsetup{compatibility=false}
-\usepackage{xcolor}
-\usepackage{soul}
-\usepackage{float}
-\usepackage{tikz-cd}
-\def\UrlFont{\rmfamily}
-
-\renewcommand \thesection{\Roman{section}}
-\renewcommand \thesubsection{\arabic{section}.\arabic{subsection}}
+\documentclass[../Paper/main.tex]{subfiles}
 
@@
 
-\title{Dynamic Modeling for Optimal Cryptoeconomic Policies}
-
-\author{Mingxuan He\\
-ECMA 33603\\
-Prof. Andre Silva
-}
-
-\maketitle
-
-\begin{abstract}
-    This paper introduces the idea of my thesis research project and documents my work so far.
-I provide a research topic description, discuss relevant literature including my replication for a baseline model, and report the current progress on my extended model, which combines two ideas from Stage 1 of the project.
-\end{abstract}
-
-%\tableofcontents
-
-\section{Introduction}
-In December 2018, the market capitalization of cryptocurrencies reached nearly 400 billion US Dollars, equivalent to 11\% of M1 in the USA \parencite{schilling2019some}.
-As the size of blockchain and cryptocurrency networks grew, there has been increasing discussion around volatility and welfare in cryptoeconomies, and ways for the issuer of the cryptocurrency protocol to implement policies to ensure there is sustainable benefits for the network of token holders.
-These policies are often referred to as the protocol's ``tokenomics".
-
-As of today, most cryptoeconomic policies are static, which means the supply of tokens grows or shrinks according to a deterministic mechanism.
-For example, the supply of Bitcoin grows at a deterministic and decreasing rate.
-Many protocols cite these static policies act as an important aspect of decentralization: as the protocol pre-commits to a set of token issuance and burning policies, it reduces the requirement for trust from users in the procotol's governance.
-However, as demonstrated by both academic literature and recent events, the lack of response mechanisms can lead to devastating results when the cryptoeconomy faces exogenous shocks.
-
-In many modern blockchain protocols, ``staking" and ``burning" are the primary coded policy rules in the underlying blockchain system.
-Staking is a mechanism where the user chooses to stake their token in the protocol for a period of time, after which the protocol rewards them with a staking yield that is paid out by newly minted tokens.
-In monetary economics terms, staking increases the total token supply by introducing new tokens into circulation, while reduces the amount of tokens in circulation due to illiquidity of the staked tokens.
-On the other hand, burning is a mechanism where the protocol burns (permanently destroys) some tokens from the supply, which usually comes from the transaction fees paid by users to conduct blockchain transactions.
-
-Current staking and burning policy rules were primarily designed for the purpose of offering user incentives and/or preventing inflation from over-issuance.
-Most importantly, they do not respond to shock factors.
-My research aims to develop a model framework where staking and burning rules can be set dynamically to maximize the welfare of relevant actors in the cryptoeconomy.
-
-This paper is organized as follows: Section \ref{sec:literature} provides an overview of the established literature.
-Section \ref{sec:model} outlines the baseline model by \citet{biais2020equilibrium} and replicates its solutions (\ref{sec:baseline}) and outlines the current progress of my extended model (\ref{sec:extensions}).
-
-\section{Literature Review}
-\label{sec:literature}
-My research is related to the emerging literature on modeling cryptocurrencies and the blockchain economy.
-Following \citet{yermack2015bitcoin} that argued that Bitcoin is not a currency, there was an interest in studying Bitcoin as a financial asset.
-\citet{athey2016bitcoin, garratt2018bitcoin, biais2020equilibrium, pagnotta2022decentralizing} studied equilibria in asset pricing models for Bitcoin.
-\citet{schilling2019some, schilling2019currency} focused on the interactions between Bitcoin and the real economy, including dollar exchange rate and currency substitution.
-A broader set of models for Bitcoin include \citet{bolt2020value, catalini2020some, hinzen2022bitcoin, chiu2017economics, huberman2021monopoly}.
-For Proof-of-Stake protocols, \citet{saleh2019volatility, saleh2021blockchain} modeled their general volatility and welfare, while \citet{catalini2020markets} examined their tokenomics in the presence of an attack.
-A common result of the aforementioned asset pricing models is that static token supply causes all shocks are absorbed by the token price, which explains the high volatility of Bitcoin.
-This provides the motivation for an endogenous token supply in my model, which adds response mechanisms in terms of dynamic policy rules therefore can potentially mitigate the price effect of exogenous shocks.
-
-Another set of literature has attempted to identify optimal policy rules for special types of tokens.
-\citet{cong2021tokenomics, cong2022token} built an asset pricing model featuring token issuance as means of platform financing and user growth leveraging network effects.
-\citet{sockin2023decentralization, sockin2023model} modeled cryptocurrencies as platform utility tokens and discussed elastic token issuance.
-\citet{d2022can} studied how stablecoin issuers can profit from seigniorage while maintaining the stablecoin's peg.
-\citet{fernandez2021central, zhu2019framework} are examples of papers proposing optimal monetary policies for CBDCs.
-While the policy goals of utility tokens are very specific (defending peg for stablecoins/CBDCs, making profit for stablecoins/platform tokens), I adopt the general policy goal of maximizing user welfare, measured by consumption and transactional benefits.
-
-My research is also related to the large literature on cryptocurrencies.
-Notable empirical researches include \cite{liu2021risks} on the risk factors of cryptocurrencies, \cite{makarov2020trading} on the arbitrage spreads among different cryptocurrency markets.
-\cite{griffin2020bitcoin} studied the relationship between Tether purchases and cryptocurrency prices.
-Studies on the microeconomics of blockchain mechanisms include \citet{budish2018economic, biais2019blockchain, gans2019more, gans2022mechanism, huberman2021monopoly}.
-
-\section{Model}
-\label{sec:model}
-
-\subsection{Baseline model}
-\label{sec:baseline}
-This model was proposed by \citeauthor*{biais2020equilibrium} in their 2020 paper in The Journal of Finance titled ``Equilibrium Bitcoin Pricing".
-Their main idea is that the fundamental value of cryptocurrencies comes from the stream of future transactional benefits (e.g.
-access to unique goods, not expropriated/taxed/constrained by government, direct internet access).
-The primary result is that Bitcoin price changes partly due to changes in fundamentals (net transactional benefits) but mostly due to extrinsic volatility.
-
-The model is a two-period cryptoeconomy with overlapping generations of users.
-The cryptoeconomy includes three representative agents (user, validator, and hacker), three financial assets (risk-free asset, standard currency, and cryptocurrency).
-It features a fixed schedule money supply.
-
-\subsubsection{Users}
-In each period, young users receive some endowment in numeraire goods, which they spend on consumption goods and the three financial assets.
-They pay a fee on any cryptocurrency purchased.
-Old users consume all their savings from the previous period and receive transactional benefits on their cryptocurrencies.
-A portion of their crypto savings gets hacked.
-The users' budget constraints are:
-
-\begin{align}
-    c_t^y &= e_t- s_t - (1+\varphi_t) q_t p_t - \hat{q}_t \hat{p}_t\\
-    c_{t+1}^o &= s_t (1+r_t) + (1-h_{t+1}) q_t p_{t+1} + \hat{q}_t \hat{p}_{t+1} \nonumber \\
-    &+ \theta_{t+1} (1-h_{t+1}) q_t p_{t+1} 
-\end{align}
-\noindent
-$e_t$: endowment\\
-$s_t$: quantity of risk-free assets held\\
-$q_t, \hat{q}_t$: quantities of crypto and dollars held\\
-$p_t, \hat{p}_t$: prices (in units of consumption goods) of crypto and dollars\\
-$h_{t+1}$: portion of crypto hacked by hackers\\
-$\varphi_t$: transaction fees involved in using crypto (exog.)\footnote{The analysis remain largely unchanged if we include a transaction cost when selling crypto in period $t+1$ as well.}\\
-$\theta_{t+1}$: transactional benefits from using crypto (exog.) (assume $\theta_{t+1}\geq-1$)
-
-\subsubsection{Validators}
-Validators receive newly minted tokens as block rewards, similar to a lump-sum transfer of money. The validators' budget constraint is:
-\begin{align}
-    c_{t+1}^v &= (X_{t+1} - X_t) p_{t+1} + \varphi_{t+1} q_{t+1} p_{t+1}
-\end{align}
-\noindent
-$X_t$: stock token supply\\
-$X_{t+1} - X_t$: increase in token supply (newly minted tokens)
-
-\subsubsection{Hackers}
-Hackers hack a portion of users' crypto. The hackers' budget constraint is:
-\begin{align}
-    c_{t+1}^h &= h_{t+1} q_t p_{t+1}
-\end{align}
-
-\noindent
-I made a graph summarizing of the interaction of the agents in two periods: Figure \ref{fig:tikz-b}.
-
-\begin{equation}
-\label{fig:tikz-b}
-\begin{tikzcd}[ampersand replacement=\&, column sep = 4.5em, row sep = 4.5em]
-Protocol 
-\ar[d, "\substack{\text{newly minted}\\\text{tokens}}" ']
-\&
-\ar[d, shift right, "\substack{\text{endow-}\\ \text{ment}}" 'near start]
-\ar[d, shift left, "\substack{\text{purchase}\\ \text{assets}}" near start]
-\&
-\ar[d, "\substack{\text{transact.}\\ \text{benefits}}" ]
-\&
-\\
-Validators
-\& 
-\substack{Young\\Users}
-\ar[l,"\substack{\text{transact.}\\ \text{fees}}" ']
-\ar[r, dashed, "t+1", 
-"\substack{\text{hold}\\\text{assets}}" ']
-\& 
-\substack{Old\\Users}
-\ar[r, "\substack{\text{hacked}\\ \text{tokens}}"]
-\&
-Hackers
-\end{tikzcd}
-\end{equation}
-
-\subsubsection{Solution}
-Here are my own steps for obtaining the pricing equations for cryptocurrency and standard currency.\\
-The market clearing condition for the three financial assets are:
-\begin{align}
-    \text{crypto: } q_t &= X_t \\
-    \text{dollars: } \hat{q}_t &= m \\
-    \text{risk-free assets: } s_t &= 0 \\
-\end{align}
-Market for consumption goods also clears (by Walras's Law):
-\begin{equation}
-    c_t^y + c_t^o + c_t^v + c_t^h = e_t
-\end{equation}
-A young user in period $t$ solves:
-\begin{align}
-\max_{s_t, q_t, \hat{q}_t} &u(c_t^y) + \beta\mathbb{E}_t u(c_{t+1}^o)\\  
-    \text{subject to  } & \text{user's budget constraints and } c_t^y \geq0 \nonumber
-\end{align}
-$^*$ Information set at period $t$ includes $ \{\theta_t, \varphi_t, \pi_t\}$ \\
-The Lagrangian is
-\begin{align}
-    \mathcal{L} = &\ u(c_t^y) + \beta\mathbb{E}_t u(c_{t+1}^o) +\lambda c_t^y \nonumber \\ 
-    = &\ u(e_t- s_t - (1+\varphi_t) q_t p_t - \hat{q}_t \hat{p}_t) \nonumber \\
-    & + \beta \mathbb{E}_t\left[u(s_t (1+r_t) + (1-h_{t+1}) q_t p_{t+1} + \hat{q}_t \hat{p}_{t+1}
-    + \theta_{t+1} (1-h_{t+1}) q_t p_{t+1}  ) \right] \nonumber \\
-    & + \lambda (e_t- s_t - (1+\varphi_t) q_t p_t - \hat{q}_t \hat{p}_t)
-\end{align}
-First-order conditions:
-\begin{align}
-    s_t: & -u'(c_t^y) + \beta(1+r_t) \mathbb{E}_t[u'(c_{t+1}^o)] = \lambda\\
-    q_t: & -(1+\varphi_t) p_t  u'(c_t^y) + \beta \mathbb{E}_t[u'(c_{t+1}^o)(1-h_{t+1})(1+\theta_{t+1})p_{t+1}] = \lambda (1+\varphi_t) p_t \\
-    \hat{q}_t: & -\hat{p}_t u'(c_t^y) + \beta \mathbb{E}_t[u'(c_{t+1}^o) \hat{p}_{t+1}] = \lambda \hat{p}_t
-\end{align}
-
-\noindent
-For Eqn. 14, substitute $\lambda$ with LHS of Eqn. 13:
-\begin{align}
-    &-(1+\varphi_t) p_t  u'(c_t^y) + \beta \mathbb{E}_t[u'(c_{t+1}^o)(1-h_{t+1})(1+\theta_{t+1})p_{t+1}] \nonumber \\
-=&\ (1+\varphi_t)p_t
-\{-u'(c_t^y) + \beta(1+r_t) \mathbb{E}_t[u'(c_{t+1}^o)]\} \\
-\Rightarrow& \nonumber \\
-&\beta \mathbb{E}_t[u'(c_{t+1}^o)(1-h_{t+1})(1+\theta_{t+1})p_{t+1}] \nonumber \\
-=&\ (1+\varphi_t)p_t\beta(1+r_t) \mathbb{E}_t[u'(c_{t+1}^o)] \\
-\Rightarrow & \nonumber \\
-p_t=&\ \frac{1}{1+r_t} \frac{1}{1+\varphi_t}\mathbb{E}_t[u'(c_{t+1}^o)]^{-1} \mathbb{E}_t[u'(c_{t+1}^o)(1-h_{t+1})(1+\theta_{t+1})p_{t+1}]
-\end{align}
-
-Eqn.
-18 is the pricing equation for cryptocurrency.
-Intuitively, $\frac{1}{1+r_t}$ is a discount by the interest rate, $1-h_{t+1}$ is the hack risk, $\frac{1+\theta_{t+1}}{1+\varphi_t}$ measures the net transactional benefits generating the currency's fundamental value, $\mathbb{E}_t[u'(c_{t+1}^o)]^{-1}u'(c_{t+1}^o)$ is the risk-neutral probability, and $p_{t+1}$ is the resale value.
-This pricing equation provides a viewpoint that Bitcoin prices reflect both fundamentals and extrinsic factors.
-
-We can also consider Eqn. 15, and substitute $\lambda$ with LHS of Eqn. 13:
-\begin{align}
-&-\hat{p}_t u'(c_t^y) + \beta \mathbb{E}_t[u'(c_{t+1}^o) \hat{p}_{t+1}] \nonumber \\
-=&\ \hat{p}_t \{-u'(c_t^y) + \beta(1+r_t) \mathbb{E}_t[u'(c_{t+1}^o)]\} \\
-\Rightarrow& \nonumber \\
-& \beta\mathbb{E}_t[u'(c_{t+1}^o) \hat{p}_{t+1}] \nonumber \\
-=&\ \hat{p}_t \beta(1+r_t) \mathbb{E}_t[u'(c_{t+1}^o)] \\
-\Rightarrow & \nonumber \\
-\hat{p}_t =&\ \frac{1}{1+r_t} \mathbb{E}_t[u'(c_{t+1}^o)]^{-1} \mathbb{E}_t[u'(c_{t+1}^o) \hat{p}_{t+1}]
-\end{align}
-
-Eqn. 21 provides an expression for the return on dollars in the cryptoeconomy, in relation to the risk-neutral probability as well as the interest rate.
-
-\subsection{Extended model}
-\label{sec:extensions}
-\subsubsection{Staking and burning}
-In my extended model, I introduce two new mechanisms:
-\begin{itemize}
-    \item Two-part transaction fee with burning
-    \item Interest-bearing staking
-\end{itemize}
-The protocol controls the staking yield (``interest rate") and the base transaction fee rate (burn rate). The figure below illustrates the new dynamics:
 \begin{equation}
@@
 \end{equation}
-Define new variables, following notation in the ideas step:\\
-$L_t$: amount of staked tokens \\
-$\delta_t$: staking yield (set by protocol)\\
-$\varphi_t^b$: base fee (set by protocol)\\
-$\varphi_t^v$: variable fee (competitively determined by validators and users)\\
-The new budget constraints are:
-\begin{align}
-    \text{Young users: } c_t^y &= e_t - s_t - (1+{\color{red} \varphi_t^b+\varphi_t^v}) q_t p_t - \hat{q}_t \hat{p}_t\\
-    \text{Old users: } c_{t+1}^o &=  s_t (1+r_t) + (1-h_{t+1}) q_t p_{t+1} + \hat{q}_t \hat{p}_{t+1} \nonumber \\
-     &\hspace{2em} + \theta_{t+1} (1-h_{t+1}) q_t p_{t+1}\\ 
-    \text{Validators: } c_{t+1}^v &= {\color{red} (1+\delta_t) L_t} p_{t+1} + {\color{red} \varphi_{t+1}^v} q_{t+1} p_{t+1} {\color{red} - L_{t+1} p_{t+1} }\\
-    \text{Hackers: } c_{t+1}^h &= h_{t+1} q_t p_{t+1}
-\end{align}
-
-\subsubsection{Endogenous token supply}
-Instead of a predetermined exogenous supply of tokens, now the supply is endogenous and dependent on the staking yield and base fee rate:
-\begin{align}
-    M_{t+1} &= (M_t - L_t) + L_t (1 + \delta_t) - \varphi_t^b X_t \nonumber \\
-    &= M_t + \delta_t L_t - \varphi_t^b X_t
-\end{align}
-$M_t$: total token supply\\
-$X_t \equiv M_t - L_t$: circulating supply (Now the market clearing condition is $X_t=q_t$)\\
-
-\subsubsection{Validator's problem}
-Since the amount staked is an active choice by the validators, we now have a new optimization problem by the validators:
-\begin{align}
-\max_{L_{t+1}}\ & u((1+\delta_t) L_t p_{t+1} + \varphi_{t+1}^v q_{t+1} p_{t+1} - L_{t+1}p_{t+1})\\
-    \text{s.t. } & q_{t+1} \leq M_{t+1} - L_{t+1} \nonumber
-\end{align}
-This problem describes the following trade off by the validators:
-\[
-\text{more staking at } t \Rightarrow
-\begin{cases}
-    \text{more staking yield at } t+1\\
-    \text{less circulating supply} \Rightarrow \text{less transact. fees at } t
-\end{cases}
-\]
-Intuitively, the budget constraint should be binding since there should not be idle tokens in the economy: all tokens either enter the circulating supply or be staked to generate yields.
-Formally, we can apply Karush-Kuhn-Tucker to solve the optimization problem.
-
-The solution to this problem, and a general equilibrium solution for the extended model, are currently work in progress.
-
-\printbibliography
 

### 2023-10-13 Presentations/lightning_slides.tex
new pitch slides

--- 2023-07-25 Presentations/pitch_slides.tex
@@
 \title[Optimal Cryptoeconomic Policies]{Dynamic Modeling for Optimal Cryptoeconomic Policies}
-\subtitle{Pitch Proposal 2}
+\subtitle{Pitch Proposal Fall 2023}
 \author{Mingxuan He}
@@
 
-\textbf{How should we design dynamic staking and burning policies?}\newline
+\textbf{How should we design dynamic staking and burning policies for Proof-of-Stake cryptoeconomies?}\newline
 \begin{itemize}
@@
         \item Pricing models of cryptocurrencies:\\
-        {\footnotesize Bitcoin: \textit{\citet{athey2016bitcoin, garratt2018bitcoin, schilling2019some, schilling2019currency, catalini2020some, biais2020equilibrium, bolt2020value, hinzen2022bitcoin, chiu2017economics}, etc.}}\\
+        {\footnotesize Bitcoin: \textit{\citet{athey2016bitcoin, garratt2018bitcoin, schilling2019some, schilling2019currency, catalini2020some, biais2023equilibrium, bolt2020value, hinzen2022bitcoin, chiu2017economics}, etc.}}\\
         {\footnotesize Proof-of-stake: \textit{\citet{catalini2020markets, saleh2019volatility, saleh2021blockchain}}}\\
@@
         \item Monetary policies for stablecoins, platform tokens, and CBDCs:\\
-        {\footnotesize \textit{\citet{cong2021tokenomics, cong2022token, d2022can, fernandez2021central, zhu2019framework, sockin2023model, sockin2023decentralization}, etc.}}\\
+        {\footnotesize \textit{\citet{cong2021tokenomics, cong2022token, cong2022staking, d2022can, fernandez2021central, zhu2019framework, sockin2023model, sockin2023decentralization}, etc.}}\\
         $\rightarrow$ \textbf{Optimizing policy for defending peg and/or making profit}
@@
 %----------------
-\section{Model (baseline)}
-\begin{frame}{The baseline model (Biais et al. 2020, Journal of Finance)}
-\textbf{Idea:} The fundamental value of crypto comes from the stream of future transactional benefits \parencite{tirole1985asset}\\
-\begin{itemize}
-    \item e.g. access to unique goods, not expropriated/taxed/constrained by government, direct internet access
-\end{itemize}
-\textbf{Setup:} Two-period model with overlapping generations
-\begin{itemize}
-    \item Three actors: users, validators (miners), hackers
-    \item Three financial assets: a risk-free asset, a standard currency (dollar), a cryptocurrency (Bitcoin)
-    \item Sources of shocks: endowment, transactional benefit, fees
-\end{itemize}
-\textbf{Result:} Bitcoin price changes partly due to changes in net transactional benefits, but mostly extrinsic volatility
-\end{frame}
+\section{Model}
+% \begin{frame}{Inspiration}
+%     \begin{figure}
+%         \includegraphics[width=0.75\textwidth]{biais_title.png}
+%     \end{figure}
+%     * Bitcoin's economic/consensus system (proof-of-work) is different from proof-of-stake
+% \end{frame}
 
-\begin{frame}{The baseline model (Biais et al. 2020, Journal of Finance)}
-\[
-\begin{tikzcd}[ampersand replacement=\&, column sep = 4.5em, row sep = 4.5em]
-Protocol 
-\ar[d, "\substack{\text{newly minted}\\\text{tokens}}" ']
-\&
-\ar[d, shift right, "\substack{\text{endow-}\\ \text{ment}}" 'near start]
-\ar[d, shift left, "\substack{\text{purchase}\\ \text{assets}}" near start]
-\&
-\ar[d, "\substack{\text{transact.}\\ \text{benefits}}" ]
-\&
-\\
-Validators
-\& 
-\substack{Young\\Users}
-\ar[l,"\substack{\text{transact.}\\ \text{fees}}" ']
-\ar[r, dashed, "t+1", 
-"\substack{\text{hold}\\\text{assets}}" ']
-\& 
-\substack{Old\\Users}
-\ar[r, "\substack{\text{hacked}\\ \text{tokens}}"]
-\&
-Hackers
-\end{tikzcd}
-\]
-In each period: %\hyperlink{formal}{\beamerbutton{Formal Problem}}
-\begin{itemize}
-    \item \textbf{Young users} receive endowment, spend on consumption goods \& financial assets. Pay fees on crypto purchased
-    \item \textbf{Old users} consume savings (some crypto savings get hacked), and receive transactional benefits
-    \item \textbf{Validators} receive newly minted tokens as block rewards
-    \item \textbf{Hackers} hack a portion of users' crypto
-\end{itemize}
-\end{frame}
-
-\begin{frame}{The baseline model: Users}
-\label{formal}
-\begin{align}
-    \text{Young users: } c_t^y &= e_t- s_t - (1+\varphi_t) q_t p_t - \hat{q}_t \hat{p}_t\\
-    \text{Old users: } c_{t+1}^o &= s_t (1+r_t) + (1-h_{t+1}) q_t p_{t+1} + \hat{q}_t \hat{p}_{t+1} \nonumber \\
-    &+ \theta_{t+1} (1-h_{t+1}) q_t p_{t+1} 
-\end{align}
-
-$e_t$: endowment\\
-$s_t$: quantity of risk-free assets held\\
-$q_t, \hat{q}_t$: quantities of crypto and dollars held\\
-$p_t, \hat{p}_t$: prices (in units of consumption goods) of crypto and dollars\\
-$h_{t+1}$: portion of crypto hacked by hackers\\
-$\varphi_t$: transaction fees involved in using crypto (exog.)\footnote{The analysis remain largely unchanged if we include a transaction cost when selling crypto in period $t+1$ as well.}\\
-$\theta_{t+1}$: transactional benefits from using crypto (exog.) (assume $\theta_{t+1}\geq-1$) \\
-
-\end{frame}
-
-\begin{frame}{The baseline model: Validators and hackers}
-\begin{align}
-    \text{Validators: } c_{t+1}^v &= (X_{t+1} - X_t) p_{t+1} + \varphi_{t+1} q_{t+1} p_{t+1}\\
-    \text{Hackers: } c_{t+1}^h &= h_{t+1} q_t p_{t+1}
-\end{align}
-$X_t$: stock token supply\\
-$X_{t+1} - X_t$: increase in token supply (newly minted tokens)
-\end{frame}
-
-\begin{frame}{The baseline model: Market clearing}
-Markets for financial assets:
-\begin{align}
-    \text{crypto: } q_t &= X_t \\
-    \text{dollars: } \hat{q}_t &= m \\
-    \text{risk-free assets: } s_t &= 0 \\
-\end{align}
-Market for consumption goods (by Walras's Law):
-\begin{equation}
-    c_t^y + c_t^o + c_t^v + c_t^h = e_t
-\end{equation}
-
-\end{frame}
-
-\begin{frame}{The baseline model: Solution}
-A young user in period $t$ solves:
-\begin{align}
-\max_{s_t, q_t, \hat{q}_t} &u(c_t^y) + \beta\mathbb{E}_t u(c_{t+1}^o)\\  
-    \text{subject to  } & \text{user's budget constraint} \nonumber
-\end{align}
-$^*$ Information set at period $t$ includes $ \{\theta_t, \varphi_t, \pi_t\}$ \\
-From FOCs obtain the equilibrium pricing equation for crypto:
-\newcommand{\vp}{\vphantom{\frac{u'(c_{t+1}^o)}{\mathbb{E}_t[u'(c_{t+1}^o)]}}}
-\begin{equation}
-    p_t = 
-    \underbrace{\vp
-    \frac{1}{1+r_t}}_\text{discount}
-    \mathbb{E}_t \Bigl[ 
-    \underbrace{\frac{u'(c_{t+1}^o)}{\mathbb{E}_t[u'(c_{t+1}^o)]}} _\text{risk-neutral prob}
-    \underbrace{\vp
-    (1-h_{t+1})} _\text{hack risk}
-    \underbrace{\vp
-    \frac{1+\theta_{t+1}}{1+\varphi_t}} _{\substack{\text{net transact.}\\ \text{benefits}}}
-     p_{t+1}
-    \Bigr]
-\end{equation}    
-\end{frame}
-
-%----------------------------------
-\section{Model (extended)}
-\begin{frame}{Extension 1: Endogenous token supply}
+\begin{frame}{A model of proof-of-stake cryptoeconomies}
     \[
@@
 \]
-I introduce:
+
 \begin{itemize}
-    \item Two-part transaction fee with burning
-    \item Interest-bearing staking
-    \item The protocol controls the staking yield (``interest rate") and the base transaction fee rate (burn rate)
+    \item Inspired by Biais et al. (J Finance 2023) ``Equilibrium Bitcoin Pricing"
+    \item Two-period OLG model
+    \item Endogenous token supply (innovation over \citet{biais2023equilibrium})
+    \item Assumption: Crypto's fundamental value comes from the stream of future transactional benefits\\
+    \begin{itemize}
+        \item e.g. access to unique goods, not expropriated/taxed/constrained by government, direct internet access
     \end{itemize}
+\end{itemize}
+
 \end{frame}
 
-\begin{frame}{Introducing staking and burning}
-$^*$ The following is work in progress\\
+\begin{frame}{User's problem}
+    \begin{itemize}
+    \item Period t: allocates endowment income $e_t^u$ into three asset classes: risk-free $s_t$, crypto $q_t$, and fiat $\hat{q}_t$.
+To buy crypto they pay a two-part transaction fee $\varphi_t^b$ (burned) and $\varphi_t^v$ (goes to validator)\\
+    \item Period t+1: receive interest $r_t$, transactional benefits $\theta_{t+1}$, and hacking loss $h_{t+1}$\\
+    \end{itemize}
 
-\textbf{Staking:}
-$L_t$: amount of staked tokens; $\delta_t$: staking yield (set by protocol)\\
-\textbf{Burning:}
-$\varphi_t^b$: base fee (set by protocol); $\varphi_t^v$: variable fee (competitively determined by validators and users)\\
-\ \\
-\textbf{New budget constraints:}
     \begin{align}
-    \text{Young users: } c_t^y &= e_t - s_t - (1+{\color{red} \varphi_t^b+\varphi_t^v}) q_t p_t - \hat{q}_t \hat{p}_t\\
-    \text{Old users: } c_{t+1}^o &=  s_t (1+r_t) + (1-h_{t+1}) q_t p_{t+1} + \hat{q}_t \hat{p}_{t+1} \nonumber \\
-     &\hspace{2em} + \theta_{t+1} (1-h_{t+1}) q_t p_{t+1}\\ 
-    \text{Validators: } c_{t+1}^v &= {\color{red} (1+\delta_t) L_t} p_{t+1} + {\color{red} \varphi_{t+1}^v} q_{t+1} p_{t+1} {\color{red} - L_{t+1} p_{t+1} }\\
-    \text{Hackers: } c_{t+1}^h &= h_{t+1} q_t p_{t+1}
+    c_t^u &= e_t^u - s_t - (1+ \varphi_t^b+\varphi_t^v) q_t p_t - \hat{q}_t \hat{p}_t\\
+    c_{t+1}^u &=  s_t (1+r_t) + (1-h_{t+1})(1+\theta_{t+1}) q_t p_{t+1} + \hat{q}_t \hat{p}_{t+1}
+    \end{align}
+
+\end{frame}
+
+\begin{frame}{Validator's problem}
+    \begin{itemize}
+        \item Period t: receive transaction fees $\varphi_t^v$, stake $L_t$
+        \item Period t+1: receive staking yield $\delta_t$
+    \end{itemize}
+    \textbf{Trade-off:}
+    \[
+    \text{more staking at } t \Rightarrow
+    \begin{cases}
+        \text{more staking yield at } t+1\\
+        \text{less circulating supply} \Rightarrow \text{less transact. fees at } t
+    \end{cases}
+    \]
+    \begin{align}
+    c_t^v &= e_t^v + \varphi_t^v q_t p_t - L_t p_t \\
+    c_{t+1}^v &= (1+\delta_t) L_t p_{t+1} 
     \end{align}
@@
 
-\begin{frame}{Token supply with staking and burning}
+\begin{frame}{Token supply}
     \begin{align}
@@
     $X_t \equiv M_t - L_t$: circulating supply \\
-\quad $\Rightarrow$ Now market clearing condition is $X_t=q_t$\\
+    \quad $\Rightarrow$ Token market clearing condition is $X_t=q_t$\\
     \ \\
@@
 
-\begin{frame}{Validator's problem}
-% should validators pay transaction fees when they cash out?
-\begin{align}
-\max_{L_{t+1}}\ & u((1+\delta_t) L_t p_{t+1} + \varphi_{t+1}^v q_{t+1} p_{t+1} - L_{t+1}p_{t+1})\\
-    \text{s.t. } & q_{t+1} \leq M_{t+1} - L_{t+1} \nonumber
-\end{align}
-\textbf{Trade-off:}
-\[
-\text{more staking at } t \Rightarrow
-\begin{cases}
-    \text{more staking yield at } t+1\\
-    \text{less circulating supply} \Rightarrow \text{less transact. fees at } t
-\end{cases}
-\]
-Apply Karush-Kuhn-Tucker to solve the optimization problem
+\begin{frame}{First order conditions}
+    * for a deterministic version of the model
+    \bigskip
+
+    User's Euler equations:
+    \begin{equation}
+        \frac{u'(c_t^u)}{u'(c_{t+1}^u)} = \beta (1+r_t) 
+        = \beta \frac{(1+\theta_{t+1})(1-h_{t+1})}{1+\varphi_t^b+\varphi_t^v} \frac{p_{t+1}}{p_t}
+        = \beta \frac{\hat{p}_{t+1}}{\hat{p}_t}
+    \end{equation}
+
+    Validator's Euler equation:
+    \begin{equation}
+        \frac{u'(c_t^v)}{u'(c_{t+1}^v)} = \beta (1+\delta_t) \frac{p_{t+1}}{p_t}
+    \end{equation}
+
+    WIP: Equilibrium solutions with stochasticity \& log/CRRA preferences
 \end{frame}
@@
 %----------------
-\section{Next Steps}
-\begin{frame}{Next Steps}
+\section{Calibration}
+\begin{frame}{Calibration (idea phase)}
     \begin{itemize}
-        \item \textbf{The model:} Finish extended model with staking and burning, obtain analytical solution for equilibrium pricing, run simulations using dynare / Python\\
-        \item \textbf{Replicate calibration:} Replicate calibration for baseline model (authors provided full replication code in Python)
-        \item \textbf{Get data on Ethereum:} 
+        \item \textbf{Data sources:} Ethereum prices from Messari API, txn fees from Dune Analytics, staking data from beaconcha.in
+        \item \textbf{Period:} Sep 2022 - now, down to block frequency (12s) 24/7
+        \item Proxy for transactional benefits/convenience yields: average onchain txn processing per second $a_t$\citep{cong2022staking}
         \begin{itemize}
-            \item ETH price data: Messari API\footnote{https://messari.io/api} (REST) and Dune Analytics\footnote{https://dune.com/docs/api} (SQL database with execution API in Python)
-            \item ETH staking and burning data: Beacon Chain\footnote{https://ethereum.github.io/beacon-APIs} (REST)
+            \item other potential proxies: Metcalfe's measure $\log(DailyActiveAddresses^2)$; \href{https://www.ncsl.org/financial-services/cryptocurrency-2023-legislation}{index on US crypto regulation (NCSL.org)}
         \end{itemize}
-        \item \textbf{Calibrate my model}: get ideas after replicating calibration
+
+        \item Proxy for hacking: manually index major hacks and wallet losses
     \end{itemize}
@@
 \section*{}
-\begin{frame}[allowframebreaks]{References}
-    \nocite{*}
+\begin{frame}[allowframebreaks, noframenumbering]{References}
+    %\nocite{*}
     %\bibliographystyle{apalike}

### 2023-11-03 Presentations/lightning_slides.tex
update slides

@@
 
-\begin{frame}{Research Question}
+\begin{frame}{Research question}
 
@@
 
-    \item Policy goal: maximize welfare for \underline{good actors}: users (increase in token price) and validators (transaction fees)
+    \item Policy goal: maximize welfare for \underline{good actors}: users (increase in token price \& consumption) and validators (transaction fees)
 \end{itemize}
@@
 
-\begin{frame}{Literature Review}
+\begin{frame}{Literature review}
     \begin{itemize}
@@
 
-\begin{frame}{Contribution to the Literature}
+\begin{frame}{Contribution to the literature}
 \begin{itemize}
-    \item Practical: Most cryptoeconomic systems feature fixed-schedule token supply
+    \item Practical: Most cryptoeconomic systems feature fixed-schedule token supply, creating highly volatile token prices
+    \item Problem: Traditional models for optimal fiscal policy (e.g.
+Ramsey) and monetary policy (e.g.
+NK) are not directly transferrable to cryptoeconomies due to transaction fee role in the cryptoeconomy
+    % \begin{itemize}
+    %     \item deterministic token supply (Bitcoin\footnote{Satoshi Nakamoto (2008). Bitcoin: A peer-to-peer electronic cash system}), 
+    %     fixed burn rate (Ethereum\footnote{Ethereum Documentation. ``Gas and Fees - Base fees"}), 
+    %     naive dynamic burning (Binance Coin)
+    % \end{itemize}
+    \item Novel hypothesis: Dynamic token supply (via staking and burning policies) can be used to optimize welfare 
     \begin{itemize}
-        \item deterministic token supply (Bitcoin\footnote{Satoshi Nakamoto (2008). Bitcoin: A peer-to-peer electronic cash system}), 
-        fixed burn rate (Ethereum\footnote{Ethereum Documentation. ``Gas and Fees - Base fees"}), 
-        naive dynamic burning (Binance Coin)
+        \item implement in a dynamic equilibrium model framework
+    \end{itemize}
 \end{itemize}
 
-    \item No published literature has been established on optimal staking and burning policies for proof-of-stake cryptocurrencies.
-\end{itemize}
-Novelty of this research:
-\begin{itemize}
-    \item Applies dynamic general equilibrium methods to model and optimize crypto policies for staking and burning            
-      \item Traditional models for optimal fiscal policy (e.g. Ramsey) and monetary policy (e.g. NK) are not directly transferrable to cryptoeconomies due to transaction fee role in the cryptoeconomy
-
-\end{itemize}
 \end{frame}
@@
 ``Proof-of-Stake Rewards and Penalties"}.
-Here I set $\alpha=1$ WLOG since $\delta_t$ is dynamic.
+Here I set $\alpha=1$ for simplicity.
     % calculations: https://blog.bitmex.com/ethereums-proof-of-stake-system-calculating-penalties-rewards/
@@
 \begin{frame}{First order conditions}    
-    * for a deterministic version of the model
+    $^*$ using a deterministic version of the model
     \bigskip
@@
 
-    WIP: Equilibrium solutions with stochasticity \& log/CRRA preferences
+    %WIP: Equilibrium solutions with stochasticity \& log/CRRA preferences
+\end{frame}
+
+\begin{frame}{Token market equilibrium}
+    \hyperlink{det_math}{\beamerbutton{Appendix: deterministic math}}
+    \begin{figure}
+        \centering
+        \includegraphics[width=\textwidth]{../Figures/det_SD.png}
+        \caption{Illustration of token market equilibrium using artificial parameters. Both supply and demand are convex in $q$}
+    \end{figure}
+
 \end{frame}
@@
 \section{Calibration}
-\begin{frame}{Calibration (idea phase)}
+
+\begin{frame}{The Ethereum (ETH) blockchain}
+    Ethereum (created by V. Buterin in 2013) is currently the second largest cryptoeconomy after Bitcoin.\\
+    \bigskip
+    Important historical upgrades to Ethereum's tokenomics:
     \begin{itemize}
-        \item \textbf{Data sources:} Ethereum prices from Messari API, txn fees from Dune Analytics, staking data from beaconcha.in
-        \item \textbf{Period:} Sep 2022 - now, down to block frequency (12s) 24/7
-        \item Proxy for transactional benefits/convenience yields: average onchain txn processing per second $a_t$\citep{cong2022staking}
+        \item London upgrade (Aug 2021): introduced base fee burning via EIP-1559
+        \item ``The Merge" (Sep 2022): transition from computing-based (PoW) to staking-based issuance (PoS) i.e. Ethereum 2.0
+        \item Shanghai-Capella upgrade (Apr 2023): unlocked withdrawls of staked ETH \footnote{Hypothesis: this changes validators' staking behaviors}
+    \end{itemize}
+\end{frame}
+
+\begin{frame}{Ethereum 2.0 data}
+    Despite having only 6-12 months of history, Ethereum 2.0 data is rich and highly accessible:
     \begin{itemize}
-            \item other potential proxies: Metcalfe's measure $\log(DailyActiveAddresses^2)$; \href{https://www.ncsl.org/financial-services/cryptocurrency-2023-legislation}{index on US crypto regulation (NCSL.org)}
+        \item All transactions are publicly broadcasted to the blockchain every 12 seconds (block time), 24/7
+        \item All validators' staking actions and rewards are also recorded
+        \item ETH-USD price data are available from both onchain sources (DEX) and offchain (CEX/``oracle") sources
     \end{itemize}
 
-        \item Proxy for hacking: manually index major hacks and wallet losses
+\end{frame}
+
+\begin{frame}{Features for calibration}
+    \begin{itemize}
+        \item Method: baseline - OLS; advanced - VAR
+        \item Data sources: Ethereum prices from Messari API, txn fees from Dune Analytics, staking data from beaconcha.in
+        \item Proxy for transactional benefits/convenience yields: 
+        \begin{itemize}
+            \item Throughput measures: average onchain txn processing per second \citep{cong2022staking}; user operations per second (new measure proposed by industry researchers)
+            \item Network-based measures: Metcalfe's measure $\log(DailyActiveAddresses^2)$; 
+            \item Additional controls: \href{https://www.ncsl.org/financial-services/cryptocurrency-2023-legislation}{index on US crypto regulation (NCSL.org)}
+        \end{itemize}
+        \item Proxy for hacking: manually index major hacks and wallet losses (problem: frequency is much lower than txn/staking actions)
     \end{itemize}
@@
 
+\section{Appendix}
+\begin{frame}[noframenumbering]{Deterministic solutions (cont.)}
+    \label{det_math}
+    \begin{align}
+        \intertext{Inverse demand curve:}
+        q_t &= \left[ \beta \frac{e_t^u}{p_t} - (1+\beta)m_t \frac{\hat{p}_t}{p_t} \right] \cdot\\
+            & \left[\beta(1+ \varphi_t^b+\varphi_t^v) + \frac{(1-h_{t+1})(1+\theta_{t+1})}{1+r_t} \frac{p_{t+1}}{p_t}\right]^{-1}\\
+        \intertext{Inverse supply curve:}
+        q_t &= \left(1+\frac{\beta}{1+\beta}\varphi_t^v\right)^{-1} \left(M_t - \frac{\beta}{1+\beta}\frac{e_t^v}{p_t}\right)
+    \end{align}
+
+\end{frame}
+
+\begin{frame}[noframenumbering]{Deterministic solutions (cont.)}
+    \begin{align}
+        \intertext{Token market clearing implies $\frac{1}{p_t^*}$ must satisfy the quadratic equation}
+        A_t \frac{1}{p_t^*} &= (M_t + B_t\frac{1}{p_t^*}) (C_t + D_t\frac{1}{p_t^*}) \\
+        \intertext{where}
+        A_t &:= \left[ \beta e_t^u - (1+\beta)m_t \hat{p}_t \right] \left(1+\frac{\beta}{1+\beta}\varphi_t^v\right);\quad
+        B_t := - \frac{\beta}{1+\beta} e_t^v;\\
+        C_t &:= \beta(1+ \varphi_t^b+\varphi_t^v);\quad
+        D_t := \frac{(1-h_{t+1})(1+\theta_{t+1})}{1+r_t} p_{t+1}
+        \end{align}
+\end{frame}
+
+\begin{frame}[noframenumbering]{Deterministic solutions (cont.)}
+    \begin{align}
+        \intertext{Therefore the closed-form solution for equilibrium token price is given by}
+        p_t^* &= \frac{2B_tD_t}{A_t-M_t D_t-B_tC_t - \sqrt{(M_t D_t+B_t C_t-A_t)^2-4M_t B_tC_tD_t}}\\
+        \intertext{under some technical conditions.}\nonumber
+    \end{align}
+
+\end{frame}
+
 \end{document}

### 2023-11-03 Paper/main.tex
some deterministic math
complete deterministic solution
fix citation year error

@@
 \renewcommand \thesubsection{\arabic{section}.\arabic{subsection}}
+\setcounter{secnumdepth}{4}
 
@@
 This paper is organized as follows: Section \ref{sec:literature} provides an overview of the established literature.
-Section \ref{sec:model} outlines the baseline model by \citet{biais2020equilibrium} and replicates its solutions (\ref{sec:baseline}) and outlines the current progress of my extended model (\ref{sec:extensions}).
+Section \ref{sec:model} outlines the baseline model by \citet{biais2023equilibrium} and replicates its solutions (\ref{sec:baseline}) and outlines the current progress of my extended model (\ref{sec:extensions}).
 Section \ref{sec:data} describes the data I plan to use for calibration.
@@
 Following \citet{yermack2015bitcoin} that argued that Bitcoin is not a currency, there was an interest in studying Bitcoin as a financial asset.
-\citet{athey2016bitcoin, garratt2018bitcoin, biais2020equilibrium, pagnotta2022decentralizing} studied equilibria in asset pricing models for Bitcoin.
+\citet{athey2016bitcoin, garratt2018bitcoin, biais2023equilibrium, pagnotta2022decentralizing} studied equilibria in asset pricing models for Bitcoin.
 \citet{schilling2019some, schilling2019currency} focused on the interactions between Bitcoin and the real economy, including dollar exchange rate and currency substitution.
@@
 \label{sec:baseline}
-This model was proposed by \citeauthor*{biais2020equilibrium} in their 2020 paper in The Journal of Finance titled ``Equilibrium Bitcoin Pricing".
+This model was proposed by \citeauthor*{biais2023equilibrium} in their 2020 paper in The Journal of Finance titled ``Equilibrium Bitcoin Pricing".
 Their main idea is that the fundamental value of cryptocurrencies comes from the stream of future transactional benefits (e.g.
@@
 I used time series data of daily ETH-USD prices provided by Messari\footnote{\url{https://messari.io/}}.
-For robustness checks, I follow \cite{biais2020equilibrium} to construct time series based on ETH prices denominated in five different currencies from 20 major exchanges.
+For robustness checks, I follow \cite{biais2023equilibrium} to construct time series based on ETH prices denominated in five different currencies from 20 major exchanges.
 For non-USD denominations, I converted the prices using daily USD exchange rates data from Federal Reserve Economic Data (FRED).
@@
 
+%--------------------Appendices--------------------
+\newpage
+\subfile{appendix}
+
 \newpage

### 2024-01-04 Paper/literature.tex
Update literature review

--- 2023-07-25 Frictions Project/frictions_step2.tex
@@
-\documentclass[12pt]{article}
-\usepackage[english]{babel}
-
-% Set page size and margins
-% Replace `letterpaper' with`a4paper' for UK/EU standard size
-\usepackage[letterpaper,top=2cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}
-
-% to typeset URLs, URIs, and DOIs
-\usepackage[colorlinks=true, allcolors=blue]{hyperref}
-\usepackage{url}
-\usepackage{graphicx}
-\usepackage[english]{babel}
-
-% Bibliography
-\usepackage[style=apa, backend=biber, natbib]{biblatex}
-\addbibresource{../references.bib}
-%\usepackage{natbib}
-
-% useful packages
-\usepackage{amsmath,amsfonts,amssymb,amsthm,mathtools,mathrsfs}
-\usepackage{caption,subcaption}
-\captionsetup{compatibility=false}
-\usepackage{xcolor}
-\usepackage{soul}
-\usepackage{float}
-\usepackage{tikz-cd}
-\def\UrlFont{\rmfamily}
-
-\renewcommand \thesection{\Roman{section}}
-\renewcommand \thesubsection{\arabic{section}.\arabic{subsection}}
+\documentclass[./main.tex]{subfiles}
+\graphicspath{{\subfix{../Figures/}}}
 
 \begin{document}
-
-\title{Dynamic Modeling for Optimal Cryptoeconomic Policies}
-
-\author{Mingxuan He\\
-ECMA 33603\\
-Prof. Andre Silva
-}
-
-\maketitle
-
-\begin{abstract}
-    This paper introduces the idea of my thesis research project and documents my work so far.
-I provide a research topic description, discuss relevant literature including my replication for a baseline model, and report the current progress on my extended model, which combines two ideas from Stage 1 of the project.
-\end{abstract}
-
-%\tableofcontents
-
-\section{Introduction}
-In December 2018, the market capitalization of cryptocurrencies reached nearly 400 billion US Dollars, equivalent to 11\% of M1 in the USA \parencite{schilling2019some}.
-As the size of blockchain and cryptocurrency networks grew, there has been increasing discussion around volatility and welfare in cryptoeconomies, and ways for the issuer of the cryptocurrency protocol to implement policies to ensure there is sustainable benefits for the network of token holders.
-These policies are often referred to as the protocol's ``tokenomics".
-
-As of today, most cryptoeconomic policies are static, which means the supply of tokens grows or shrinks according to a deterministic mechanism.
-For example, the supply of Bitcoin grows at a deterministic and decreasing rate.
-Many protocols cite these static policies act as an important aspect of decentralization: as the protocol pre-commits to a set of token issuance and burning policies, it reduces the requirement for trust from users in the procotol's governance.
-However, as demonstrated by both academic literature and recent events, the lack of response mechanisms can lead to devastating results when the cryptoeconomy faces exogenous shocks.
-
-In many modern blockchain protocols, ``staking" and ``burning" are the primary coded policy rules in the underlying blockchain system.
-Staking is a mechanism where the user chooses to stake their token in the protocol for a period of time, after which the protocol rewards them with a staking yield that is paid out by newly minted tokens.
-In monetary economics terms, staking increases the total token supply by introducing new tokens into circulation, while reduces the amount of tokens in circulation due to illiquidity of the staked tokens.
-On the other hand, burning is a mechanism where the protocol burns (permanently destroys) some tokens from the supply, which usually comes from the transaction fees paid by users to conduct blockchain transactions.
-
-Current staking and burning policy rules were primarily designed for the purpose of offering user incentives and/or preventing inflation from over-issuance.
-Most importantly, they do not respond to shock factors.
-My research aims to develop a model framework where staking and burning rules can be set dynamically to maximize the welfare of relevant actors in the cryptoeconomy.
-
-This paper is organized as follows: Section \ref{sec:literature} provides an overview of the established literature.
-Section \ref{sec:model} outlines the baseline model by \citet{biais2020equilibrium} and replicates its solutions (\ref{sec:baseline}) and outlines the current progress of my extended model (\ref{sec:extensions}).
 
@@
 Following \citet{yermack2015bitcoin} that argued that Bitcoin is not a currency, there was an interest in studying Bitcoin as a financial asset.
-\citet{athey2016bitcoin, garratt2018bitcoin, biais2020equilibrium, pagnotta2022decentralizing} studied equilibria in asset pricing models for Bitcoin.
+\citet{athey2016bitcoin, garratt2018bitcoin, biais2023equilibrium, pagnotta2022decentralizing} studied equilibria in asset pricing models for Bitcoin.
 \citet{schilling2019some, schilling2019currency} focused on the interactions between Bitcoin and the real economy, including dollar exchange rate and currency substitution.
 A broader set of models for Bitcoin include \citet{bolt2020value, catalini2020some, hinzen2022bitcoin, chiu2017economics, huberman2021monopoly}.
-For Proof-of-Stake protocols, \citet{saleh2019volatility, saleh2021blockchain} modeled their general volatility and welfare, while \citet{catalini2020markets} examined their tokenomics in the presence of an attack.
-A common result of the aforementioned asset pricing models is that static token supply causes all shocks are absorbed by the token price, which explains the high volatility of Bitcoin.
+For proof-of-stake protocols, \citet{saleh2019volatility, saleh2021blockchain} modeled their general volatility and welfare, while \citet{catalini2020markets} examined their tokenomics in the presence of an attack.
+A common result of the aforementioned asset pricing models is that static token supply causes all shocks to be absorbed by the token price, which explains the high volatility of Bitcoin.
 This provides the motivation for an endogenous token supply in my model, which adds response mechanisms in terms of dynamic policy rules therefore can potentially mitigate the price effect of exogenous shocks.
@@
 
+Two recent papers closely related to mine are \citet{cong2022staking} and \citet{jermann2023macro}.
+\citet{cong2022staking} applied their dynamic portfolio model to a variety of proof-of-stake blockchains, with a focus on the relationship between equilibrium staking and token carry.
+Differing from their model, mine features endogenous token supply and emphasizes policy control in response to exogenous shocks.
+\citet{jermann2023macro} built a macrofinance model for the Ethereum blockchain, characterizing an equilibrium staking ratio that is dependent on transactional benefits and gas fees.
+It discussed two separate policy tools: functional form of the staking yield and staking yield, while I frame the policymaker problem as adjusting both staking yields and burning rates.
+
 My research is also related to the large literature on cryptocurrencies.
@@
 
-\section{Model}
-\label{sec:model}
-
-\subsection{Baseline model}
-\label{sec:baseline}
-This model was proposed by \citeauthor*{biais2020equilibrium} in their 2020 paper in The Journal of Finance titled ``Equilibrium Bitcoin Pricing".
-Their main idea is that the fundamental value of cryptocurrencies comes from the stream of future transactional benefits (e.g.
-access to unique goods, not expropriated/taxed/constrained by government, direct internet access).
-The primary result is that Bitcoin price changes partly due to changes in fundamentals (net transactional benefits) but mostly due to extrinsic volatility.
-
-The model is a two-period cryptoeconomy with overlapping generations of users.
-The cryptoeconomy includes three representative agents (user, validator, and hacker), three financial assets (risk-free asset, standard currency, and cryptocurrency).
-It features a fixed schedule money supply.
-
-\subsubsection{Users}
-In each period, young users receive some endowment in numeraire goods, which they spend on consumption goods and the three financial assets.
-They pay a fee on any cryptocurrency purchased.
-Old users consume all their savings from the previous period and receive transactional benefits on their cryptocurrencies.
-A portion of their crypto savings gets hacked.
-The users' budget constraints are:
-
-\begin{align}
-    c_t^y &= e_t- s_t - (1+\varphi_t) q_t p_t - \hat{q}_t \hat{p}_t\\
-    c_{t+1}^o &= s_t (1+r_t) + (1-h_{t+1}) q_t p_{t+1} + \hat{q}_t \hat{p}_{t+1} \nonumber \\
-    &+ \theta_{t+1} (1-h_{t+1}) q_t p_{t+1} 
-\end{align}
-\noindent
-$e_t$: endowment\\
-$s_t$: quantity of risk-free assets held\\
-$q_t, \hat{q}_t$: quantities of crypto and dollars held\\
-$p_t, \hat{p}_t$: prices (in units of consumption goods) of crypto and dollars\\
-$h_{t+1}$: portion of crypto hacked by hackers\\
-$\varphi_t$: transaction fees involved in using crypto (exog.)\footnote{The analysis remain largely unchanged if we include a transaction cost when selling crypto in period $t+1$ as well.}\\
-$\theta_{t+1}$: transactional benefits from using crypto (exog.) (assume $\theta_{t+1}\geq-1$)
-
-\subsubsection{Validators}
-Validators receive newly minted tokens as block rewards, similar to a lump-sum transfer of money. The validators' budget constraint is:
-\begin{align}
-    c_{t+1}^v &= (X_{t+1} - X_t) p_{t+1} + \varphi_{t+1} q_{t+1} p_{t+1}
-\end{align}
-\noindent
-$X_t$: stock token supply\\
-$X_{t+1} - X_t$: increase in token supply (newly minted tokens)
-
-\subsubsection{Hackers}
-Hackers hack a portion of users' crypto. The hackers' budget constraint is:
-\begin{align}
-    c_{t+1}^h &= h_{t+1} q_t p_{t+1}
-\end{align}
-
-\noindent
-I made a graph summarizing of the interaction of the agents in two periods: Figure \ref{fig:tikz-b}.
-
-\begin{equation}
-\label{fig:tikz-b}
-\begin{tikzcd}[ampersand replacement=\&, column sep = 4.5em, row sep = 4.5em]
-Protocol 
-\ar[d, "\substack{\text{newly minted}\\\text{tokens}}" ']
-\&
-\ar[d, shift right, "\substack{\text{endow-}\\ \text{ment}}" 'near start]
-\ar[d, shift left, "\substack{\text{purchase}\\ \text{assets}}" near start]
-\&
-\ar[d, "\substack{\text{transact.}\\ \text{benefits}}" ]
-\&
-\\
-Validators
-\& 
-\substack{Young\\Users}
-\ar[l,"\substack{\text{transact.}\\ \text{fees}}" ']
-\ar[r, dashed, "t+1", 
-"\substack{\text{hold}\\\text{assets}}" ']
-\& 
-\substack{Old\\Users}
-\ar[r, "\substack{\text{hacked}\\ \text{tokens}}"]
-\&
-Hackers
-\end{tikzcd}
-\end{equation}
-
-\subsubsection{Solution}
-Here are my own steps for obtaining the pricing equations for cryptocurrency and standard currency.\\
-The market clearing condition for the three financial assets are:
-\begin{align}
-    \text{crypto: } q_t &= X_t \\
-    \text{dollars: } \hat{q}_t &= m \\
-    \text{risk-free assets: } s_t &= 0 \\
-\end{align}
-Market for consumption goods also clears (by Walras's Law):
-\begin{equation}
-    c_t^y + c_t^o + c_t^v + c_t^h = e_t
-\end{equation}
-A young user in period $t$ solves:
-\begin{align}
-\max_{s_t, q_t, \hat{q}_t} &u(c_t^y) + \beta\mathbb{E}_t u(c_{t+1}^o)\\  
-    \text{subject to  } & \text{user's budget constraints and } c_t^y \geq0 \nonumber
-\end{align}
-$^*$ Information set at period $t$ includes $ \{\theta_t, \varphi_t, \pi_t\}$ \\
-The Lagrangian is
-\begin{align}
-    \mathcal{L} = &\ u(c_t^y) + \beta\mathbb{E}_t u(c_{t+1}^o) +\lambda c_t^y \nonumber \\ 
-    = &\ u(e_t- s_t - (1+\varphi_t) q_t p_t - \hat{q}_t \hat{p}_t) \nonumber \\
-    & + \beta \mathbb{E}_t\left[u(s_t (1+r_t) + (1-h_{t+1}) q_t p_{t+1} + \hat{q}_t \hat{p}_{t+1}
-    + \theta_{t+1} (1-h_{t+1}) q_t p_{t+1}  ) \right] \nonumber \\
-    & + \lambda (e_t- s_t - (1+\varphi_t) q_t p_t - \hat{q}_t \hat{p}_t)
-\end{align}
-First-order conditions:
-\begin{align}
-    s_t: & -u'(c_t^y) + \beta(1+r_t) \mathbb{E}_t[u'(c_{t+1}^o)] = \lambda\\
-    q_t: & -(1+\varphi_t) p_t  u'(c_t^y) + \beta \mathbb{E}_t[u'(c_{t+1}^o)(1-h_{t+1})(1+\theta_{t+1})p_{t+1}] = \lambda (1+\varphi_t) p_t \\
-    \hat{q}_t: & -\hat{p}_t u'(c_t^y) + \beta \mathbb{E}_t[u'(c_{t+1}^o) \hat{p}_{t+1}] = \lambda \hat{p}_t
-\end{align}
-
-\noindent
-For Eqn. 14, substitute $\lambda$ with LHS of Eqn. 13:
-\begin{align}
-    &-(1+\varphi_t) p_t  u'(c_t^y) + \beta \mathbb{E}_t[u'(c_{t+1}^o)(1-h_{t+1})(1+\theta_{t+1})p_{t+1}] \nonumber \\
-=&\ (1+\varphi_t)p_t
-\{-u'(c_t^y) + \beta(1+r_t) \mathbb{E}_t[u'(c_{t+1}^o)]\} \\
-\Rightarrow& \nonumber \\
-&\beta \mathbb{E}_t[u'(c_{t+1}^o)(1-h_{t+1})(1+\theta_{t+1})p_{t+1}] \nonumber \\
-=&\ (1+\varphi_t)p_t\beta(1+r_t) \mathbb{E}_t[u'(c_{t+1}^o)] \\
-\Rightarrow & \nonumber \\
-p_t=&\ \frac{1}{1+r_t} \frac{1}{1+\varphi_t}\mathbb{E}_t[u'(c_{t+1}^o)]^{-1} \mathbb{E}_t[u'(c_{t+1}^o)(1-h_{t+1})(1+\theta_{t+1})p_{t+1}]
-\end{align}
-
-Eqn.
-18 is the pricing equation for cryptocurrency.
-Intuitively, $\frac{1}{1+r_t}$ is a discount by the interest rate, $1-h_{t+1}$ is the hack risk, $\frac{1+\theta_{t+1}}{1+\varphi_t}$ measures the net transactional benefits generating the currency's fundamental value, $\mathbb{E}_t[u'(c_{t+1}^o)]^{-1}u'(c_{t+1}^o)$ is the risk-neutral probability, and $p_{t+1}$ is the resale value.
-This pricing equation provides a viewpoint that Bitcoin prices reflect both fundamentals and extrinsic factors.
-
-We can also consider Eqn. 15, and substitute $\lambda$ with LHS of Eqn. 13:
-\begin{align}
-&-\hat{p}_t u'(c_t^y) + \beta \mathbb{E}_t[u'(c_{t+1}^o) \hat{p}_{t+1}] \nonumber \\
-=&\ \hat{p}_t \{-u'(c_t^y) + \beta(1+r_t) \mathbb{E}_t[u'(c_{t+1}^o)]\} \\
-\Rightarrow& \nonumber \\
-& \beta\mathbb{E}_t[u'(c_{t+1}^o) \hat{p}_{t+1}] \nonumber \\
-=&\ \hat{p}_t \beta(1+r_t) \mathbb{E}_t[u'(c_{t+1}^o)] \\
-\Rightarrow & \nonumber \\
-\hat{p}_t =&\ \frac{1}{1+r_t} \mathbb{E}_t[u'(c_{t+1}^o)]^{-1} \mathbb{E}_t[u'(c_{t+1}^o) \hat{p}_{t+1}]
-\end{align}
-
-Eqn. 21 provides an expression for the return on dollars in the cryptoeconomy, in relation to the risk-neutral probability as well as the interest rate.
-
-\subsection{Extended model}
-\label{sec:extensions}
-\subsubsection{Staking and burning}
-In my extended model, I introduce two new mechanisms:
-\begin{itemize}
-    \item Two-part transaction fee with burning
-    \item Interest-bearing staking
-\end{itemize}
-The protocol controls the staking yield (``interest rate") and the base transaction fee rate (burn rate). The figure below illustrates the new dynamics:
-\begin{equation}
-    \begin{tikzcd}[ampersand replacement=\&, column sep = 4.5em, row sep = 4.5em]
-Protocol 
-\ar[d, shift right, "\substack{\text{newly minted}\\\text{tokens}\\(t+1)}" ']
-\&
-\ar[d, shift right, "\substack{\text{endow-}\\\text{ment}}" 'near start]
-\ar[d, shift left, "\substack{\text{purchase}\\ \text{assets}}" near start]
-\&
-\ar[d, "\substack{\text{transact.}\\ \text{benefits}}" ]
-\&
-\\
-Validators
-\ar[u, shift right, red, "\substack{\text{stake}\\\text{tokens}\\(t)}" ' red ]
-\& 
-\substack{Young\\Users}
-\ar[l,"\substack{\text{variable}\\ \text{fees (``tip")}}" ']
-\ar[lu, red, "\substack{\text{base fees}\\ \text{(burned)}}" {sloped,auto}' red]
-\ar[r, dashed, "t+1", 
-"\substack{\text{hold}\\\text{assets}}" ']
-\& 
-\substack{Old\\Users}
-\ar[r, "\substack{\text{hacked}\\ \text{tokens}}"]
-\&
-Hackers
-\end{tikzcd}
-\end{equation}
-Define new variables, following notation in the ideas step:\\
-$L_t$: amount of staked tokens \\
-$\delta_t$: staking yield (set by protocol)\\
-$\varphi_t^b$: base fee (set by protocol)\\
-$\varphi_t^v$: variable fee (competitively determined by validators and users)\\
-The new budget constraints are:
-\begin{align}
-    \text{Young users: } c_t^y &= e_t - s_t - (1+{\color{red} \varphi_t^b+\varphi_t^v}) q_t p_t - \hat{q}_t \hat{p}_t\\
-    \text{Old users: } c_{t+1}^o &=  s_t (1+r_t) + (1-h_{t+1}) q_t p_{t+1} + \hat{q}_t \hat{p}_{t+1} \nonumber \\
-     &\hspace{2em} + \theta_{t+1} (1-h_{t+1}) q_t p_{t+1}\\ 
-    \text{Validators: } c_{t+1}^v &= {\color{red} (1+\delta_t) L_t} p_{t+1} + {\color{red} \varphi_{t+1}^v} q_{t+1} p_{t+1} {\color{red} - L_{t+1} p_{t+1} }\\
-    \text{Hackers: } c_{t+1}^h &= h_{t+1} q_t p_{t+1}
-\end{align}
-
-\subsubsection{Endogenous token supply}
-Instead of a predetermined exogenous supply of tokens, now the supply is endogenous and dependent on the staking yield and base fee rate:
-\begin{align}
-    M_{t+1} &= (M_t - L_t) + L_t (1 + \delta_t) - \varphi_t^b X_t \nonumber \\
-    &= M_t + \delta_t L_t - \varphi_t^b X_t
-\end{align}
-$M_t$: total token supply\\
-$X_t \equiv M_t - L_t$: circulating supply (Now the market clearing condition is $X_t=q_t$)\\
-
-\subsubsection{Validator's problem}
-Since the amount staked is an active choice by the validators, we now have a new optimization problem by the validators:
-\begin{align}
-\max_{L_{t+1}}\ & u((1+\delta_t) L_t p_{t+1} + \varphi_{t+1}^v q_{t+1} p_{t+1} - L_{t+1}p_{t+1})\\
-    \text{s.t. } & q_{t+1} \leq M_{t+1} - L_{t+1} \nonumber
-\end{align}
-This problem describes the following trade off by the validators:
-\[
-\text{more staking at } t \Rightarrow
-\begin{cases}
-    \text{more staking yield at } t+1\\
-    \text{less circulating supply} \Rightarrow \text{less transact. fees at } t
-\end{cases}
-\]
-Intuitively, the budget constraint should be binding since there should not be idle tokens in the economy: all tokens either enter the circulating supply or be staked to generate yields.
-Formally, we can apply Karush-Kuhn-Tucker to solve the optimization problem.
-
-The solution to this problem, and a general equilibrium solution for the extended model, are currently work in progress.
-
-\printbibliography
-
 \end{document}

### 2024-01-04 Paper/main.tex
update data sources

@@
 
-\section{Literature Review}
-\label{sec:literature}
-% TODO: add new William Cong paper
-My research is related to the emerging literature on modeling cryptocurrencies and the blockchain economy.
-Following \citet{yermack2015bitcoin} that argued that Bitcoin is not a currency, there was an interest in studying Bitcoin as a financial asset.
-\citet{athey2016bitcoin, garratt2018bitcoin, biais2023equilibrium, pagnotta2022decentralizing} studied equilibria in asset pricing models for Bitcoin.
-\citet{schilling2019some, schilling2019currency} focused on the interactions between Bitcoin and the real economy, including dollar exchange rate and currency substitution.
-A broader set of models for Bitcoin include \citet{bolt2020value, catalini2020some, hinzen2022bitcoin, chiu2017economics, huberman2021monopoly}.
-For Proof-of-Stake protocols, \citet{saleh2019volatility, saleh2021blockchain} modeled their general volatility and welfare, while \citet{catalini2020markets} examined their tokenomics in the presence of an attack.
-A common result of the aforementioned asset pricing models is that static token supply causes all shocks are absorbed by the token price, which explains the high volatility of Bitcoin.
-This provides the motivation for an endogenous token supply in my model, which adds response mechanisms in terms of dynamic policy rules therefore can potentially mitigate the price effect of exogenous shocks.
-
-Another set of literature has attempted to identify optimal policy rules for special types of tokens.
-\citet{cong2021tokenomics, cong2022token} built an asset pricing model featuring token issuance as means of platform financing and user growth leveraging network effects.
-\citet{sockin2023decentralization, sockin2023model} modeled cryptocurrencies as platform utility tokens and discussed elastic token issuance.
-\citet{d2022can} studied how stablecoin issuers can profit from seigniorage while maintaining the stablecoin's peg.
-\citet{fernandez2021central, zhu2019framework} are examples of papers proposing optimal monetary policies for CBDCs.
-While the policy goals of utility tokens are very specific (defending peg for stablecoins/CBDCs, making profit for stablecoins/platform tokens), I adopt the general policy goal of maximizing user welfare, measured by consumption and transactional benefits.
-
-My research is also related to the large literature on cryptocurrencies.
-Notable empirical researches include \cite{liu2021risks} on the risk factors of cryptocurrencies, \cite{makarov2020trading} on the arbitrage spreads among different cryptocurrency markets.
-\cite{griffin2020bitcoin} studied the relationship between Tether purchases and cryptocurrency prices.
-Studies on the microeconomics of blockchain mechanisms include \citet{budish2018economic, biais2019blockchain, gans2019more, gans2022mechanism, huberman2021monopoly}.
+\subfile{literature}
 
@@
 $\varphi_t^b$: base fee (set by protocol)\\
-$\varphi_t^v$: variable fee (competitively determined by validators and users)\\
+$\varphi_t^v$: variable fee (exogenously determined by the market for block spaces)\\
 
@@
 
-The solution to this problem, and a general equilibrium solution for the extended model, are currently work in progress.
+In the Appendix, I outline the solution to a deterministic version of the model.
 
@@
 
-Ether is the native token of the Ethereum protocol, which was originally founded in 2014 by Vitalik Buterin as a Proof-of-Work blockchain.
+Ether is the native token of the Ethereum protocol, which was originally founded in 2014 by Vitalik Buterin as a proof-of-work blockchain.
 In August 2021, the Ethereum blockchain implemented an upgrade referred to as Ethereum Improvement Proposal \#1559 or EIP-1559.
 EIP-1559 introduced a two-part transaction fee mechanism with an instantly-burned ``base fee" for their transactions to be included in the next block, and a ``priority fee" to pay validators for faster inclusion.
-In September 2022, Ethereum migrated from a Proof-of-Work (PoW) to Proof-of-Stake (PoS) consensus model (commonly known as ``the Merge"), mandating validator staking as the only source of new ETH tokens.
+In September 2022, Ethereum migrated from a proof-of-work (PoW) to proof-of-stake (PoS) consensus model (commonly known as ``the Merge"), mandating validator staking as the only source of new ETH tokens.
 Staking and burning together controls the supply of ETH on the blockchain.
@@
 By design of the Ethereum blockchain, information on all historical transactions are publicly visible onchain.
-For each transaction, I retrieved its value and the associated base fee and priority fee through onchain data provider Dune Analytics\footnote{\url{https://dune.com/}}.
+For each transaction, I retrieved its value and the associated base fee and priority fee through onchain data provider Etherscan\footnote{\url{https://etherscan.io/}}.
 Daily transaction volumes are computed by summing the value of all transactions in that day.
@@
 
+\section{Calibration}
+This is work in progress.
+
 %--------------------Appendices--------------------
